\documentclass[11pt]{My_preprint}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title & Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\title{The hybrid model for arbitrary dispersed multiphase flows with surface properties}
\title{Averaged equations for disperse axi-symmetric fluid particles }

\author[1,2]{Nicolas Fintzi}
\author[1]{Jean-Lou Pierson}
% \author[2]{Stephane Popinet}
\author[2]{Daniel Lhuillier}
\affil[1]{IFP Energies Nouvelles, Rond-point de l’changeur de Solaize, 69360 Solaize}
\affil[2]{Sorbonne Université, Institut Jean le Rond ∂’Alembert, 4 place Jussieu, 75252 PARIS CEDEX 05, France}


\begin{document}

\maketitle

\begin{abstract}
    This article presents a comprehensive study of the averaged equations for dispersed multiphase flows.
    We present a systematic derivation of a general averaged hybrid model that incorporates the influence of internal properties and surface properties of arbitrary particles dispersed in a continuous phase.
    The dispersed phase averaged equations are derived using two distinct formalism :
    the particle-average or Lagrangian formalism proposed by \citet{zhang1994ensemble,jackson1997locally};
    and the phase-average method, which is also employed for the continuous phase based on the approach of \citet{drew1983mathematical}. 
    The particle-phase averaged formalism yields the conventional linear conservation equations, as well as the less familiar moments' conservation equations.
    The primary contribution is the demonstration of the equivalence between the particle-averaged and phase-averaged equations. 
    We show that the phase-averaged equation of the dispersed phase, is in fact a series expansion of the so-called particle-averaged moments equations. 
    The second contribution of this work is the global derivation of linear and moments equations of the particle phase in their most generalized form, the link to the continuous phase is also made. 
    We expose the mass, momentum and energy equations for both phases and investigate where does the contribution of the particle inner and surface stresses impact these equations. 
    % We demonstrate where does the stress and surface tension stresses plays a role in the particles balance equations. 
    % Consequently, as first stated by \citet{zhang1997momentum} and \citet{lhuillier2000bilan}, we proved that by incorporating an arbitrary number of moment equations, we can achieve an arbitrary order of accuracy in the modeling of the dispersed phase.
    Additionally, it is shown how energy transfer take place across scales and phases within a dispersed model, correcting a misconception regarding the diffusive fluxes. 
    To illustrate that we choose two specific example : a suspension of cylinders where we focus on the modeling of the rotational motion and averaged inertia martix transport. 
    The second case is the case of spherical rising droplets were we point out the impact of the internal motion on the pseudo turbulent equation. 
    % Finally, to provide a practical application and enhance the understanding of the first-moments conservation laws, we propose to study various examples.
    % In particular, we demonstrate how to derive a hybrid model capable to predict the distribution of surfactant over the interface of bubbles in contaminated rising bubbly flows.
    The closure problem isn't solved here. 
    Instead, the ambition of the manuscript is to provide a set of equation adaptable to any flow kind and discuss the various form it can takes depending on the particle nature. 
    Overall we provide a clear dispersed two-phase flow hybrid models for arbitrary particles. 
\end{abstract}



\input{Closure_hybrid/introduction.tex}
%\section{The two-fluid model}
% \section{Eulerian equation of motion}
\section{Local scale equations}
\label{sec:two-fluid}
\input{Closure_hybrid/Local_scale_laws_simple.tex}

\section{Lagrangian equations for the dispersed phase}
\label{sec:Lagrangian}
\input{Closure_hybrid/Lagrangian_description.tex}
% \input{Closure_hybrid/Single_Ellipse_1.tex}
% \input{Closure_hybrid/Single_Ellipse_3.tex}
\input{Closure_hybrid/Single_Ellipse_4.tex}
% \input{Closure_hybrid/Lagrange_to_euler.tex}

\section{The hybrid model}
\label{sec:averaged_eq}
\tb{expose the avg equaiton under the form of the particles phase exposed above }
\tb{ Maybe do the local reference frame avg eq }
\tb{ Explain that these need closure and that the kinetic internal eq can be used for the shape as well }
\tb{ Then the form of some closure is derived in appendix }
% \input{Closure_hybrid/Averaged_laws.tex}
% \input{Closure_hybrid/Equivalence.tex}
\input{Closure_hybrid/Bulk_stress_ellipse.tex}
% \input{Closure_hybrid/Hybrid_model.tex}



\section{Examples and applications}
% \section{Monodisperse emulsion of rising spherical droplets.}
\label{sec:Exemples}

% \input{Closure_hybrid/Dimensionless.tex}
% \input{Closure_hybrid/Conditional_avg.tex}
\input{Closure_hybrid/Spherical.tex}
\input{Closure_hybrid/Internal.tex}
\input{Closure_hybrid/Ellipsoid_3.tex}

% \input{Closure_hybrid/Ellipsoid_2.tex}
% \input{Closure_hybrid/Ellipsoid.tex}
% % \input{Closure_hybrid/Axis_symmetric_part.tex}
% \input{Closure_hybrid/Disscusion.tex}


% \input{Closure_hybrid/Brouillion.tex}
% \input{Closure_hybrid/Application_again2.tex}


% \input{Closure_hybrid/Application.tex}
% \input{Closure_hybrid/Application_stress.tex}
% \section{Examples and applications}




\section{Discussion and conclusion}
\begin{itemize}
\item We clarified the momentum stress components for dorps
\begin{itemize}
    \item The extra deformation tensor is acctually part of the stresslet definition.
\end{itemize}
\item The energy equaiton is derived for fluid particle
\begin{itemize}
    \item We make appear the source terms clearly.
    \item We distinguish the differents contributions. 
\end{itemize}
\item Special application to Hill vortecies
\item Mention of other applications
\end{itemize}
\input{Closure_hybrid/Conclusion.tex}

\section*{Acknowledgement}
We would like to express our sincere gratitude to Professor D. Lhuillier for his inspiring and insightful class, which has greatly influenced our work.
Also, the authors are grateful for many in-depth discussions with Professor St\'ephane Popinet from \textit{Institut Jean le Rond Alembert} as well. 
\bibliography{Bib/bib_bulles.bib}



\appendix

% \input{Closure_hybrid/Singularity.tex}
% \input{Closure_hybrid/Velocity_definition.tex}
% \input{Closure_hybrid/Arbitrary_moments_eq.tex}

\input{Closure_hybrid/A_droplet_in_shear_flow.tex}

\end{document}
