\documentclass[11pt]{My_preprint}
\usepackage{listing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title & Author %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\title{
%    Particle resolved simulation of buoyancy driven motion of monodisperse drops: microstructure modeling with Nearest particle statistics.
%    }
\title{
Buoyancy driven motion of non-coalescing inertial drops: microstructure modeling with nearest particle statistics. %nearest particle microstructure.
    }

\author[1,2]{Nicolas Fintzi}
\author[1]{Jean-Lou Pierson}
\author[2]{Stephane Popinet}
\affil[1]{IFP Energies Nouvelles, Rond-point de l’echangeur de Solaize, 69360 Solaize}
\affil[2]{Sorbonne Universit\'e, Institut Jean le Rond d'Alembert, 4 place Jussieu, 75252 PARIS CEDEX 05, France}
\normalmarginpar


\begin{document}

\maketitle

\begin{abstract}
    In this study, we provide a comprehensive analysis of the various  arrangements that droplets can adopt within dispersed buoyant emulsions. 
    This is termed the study of the microstructure.
    % The study treat both the numerical and theoretical aspects.
    % in a kinetic-theory-like framework.
    To this end, we have developed a novel algorithm capable of effectively prevents numerical coalesce between drops at reasonable computational cost.
    This algorithm is implemented within the Volume of Fluid (VoF) method, utilizing the \href{http://basilisk.fr}{http://basilisk.fr} open source code. 
    Subsequently, we conducted Direct Numerical Simulations (DNS) of statistically steady state mono-disperse buoyant emulsion, over a broad range of \textit{Galileo} number ($Ga$), particle volume fraction ($\phi$), and viscosity ratio ($\lambda$). 
    The density ratio and the \textit{Bond} number are kept constant, $\zeta = 1.11$ and  $Bo = 0.2$, respectively. 
    % In \citet{zhang2023evolution}, it is demonstrated that the microstructure can be characterized effectively using the nearest particle statistic.
    % This approach relies solely on the tensor quantity, \textbf{R}, which represents the second moment of the nearest particle pair distribution.
    % Then, we revisit the \textit{nearest particle statistics} framework of \citet{zhang2023evolution}.
    Then it is shown that, as predicted by \citet{zhang2023evolution}, the second moment of the nearest particle pair distribution, noted \textbf{R}, has the capability to quantify microstructure's features such as clusters and layers of particles.
    In particular, it is found that : 
    (1) At low $Ga$ isotropic clusters appear with increasing $\phi$. 
    (2) Non-isotropic clusters such as layers of particles, are more likely to form for high \textit{Galileo} number.
    (3) The viscosity ratio $\lambda$ has an important impact on the microstructure, clearly more layers are formed for $\lambda = 1$ than $\lambda = 10$. 
    Following this, it is  demonstrated that \textbf{R} follow a kinetic theory-like conservation equation and is governed by a relaxation time $\tau_p$, which is also the average time of interaction between nearest particles pairs. 
    It is shown that $\tau_p$ is higher for $\lambda = 1$ than 
    $\lambda = 10$, and even lower for solid particles at same $Ga$ and $\phi$.
    After, a meticulous analysis of the averaged relative velocity fields between nearest neighbors, we could infer that mechanism such as \textit{Drafting Kissing Tumbling} \citep{fortes1987nonlinear} were present in buoyant emulsions, and that it contribute partly to the formation of the microstructure.
    % Additionally, other behavior are identified in these systems. 
    Overall, our study provides a measure of the microstructure geometry and relaxation time, in terms of $Ga$, $\phi$ and $\lambda$. 
\end{abstract}

\input{microstructure/Introduction.tex}

\section{Numerical methodology}
\label{sec:methodo}

In this section we expose the strategy employed to conduct statistically steady state simulations of rising mono-disperse suspension of droplets in a fully periodic domain. 
We start by introducing the physical parameter, followed by a description of the numerical methods.
Lastly, we detail the methodology adopted to collect statistics about microstructure, which are presented in the next sections.

The source code used to perform the DNS is entirely open source.
The simulations are running within the \texttt{Basilisk C} framework, (see \href{http://basilisk.fr}{basilisk.fr}), which is an extension of the C programming language, adapted for the solution of partial differential equations on Cartesian meshes. 
Note that this section is complemented by the wiki page, \href{http://basilisk.fr/sandbox/fintzin/Rising-Suspenion/RS.c}{RS.c}, where the reader can access the source code used to conduct the DNS, as well as comments and notes to help comprehension. 
\tb{la page wiki n'est pas à jour}

\input{microstructure/Problem_statement.tex}
\input{microstructure/Simulation_Setup.tex}
\input{microstructure/no_coalesence.tex}




\section{The nearest particle statistics}

\input{microstructure/The_nearest_particle_statistics.tex}


\section{The microstructure}
\label{sec:microstructure}
\input{microstructure/Non_Inertial.tex}
\input{microstructure/Inertial.tex}


\section{Conclusion}
\input{microstructure/conclusion.tex}

\appendix
%\section{Statistical convergence and mesh independence studies}
\section{Numerical validations}
\label{ap:validation}
\input{microstructure/validation.tex}
% \input{microstructure/Appendix1.tex}

\input{microstructure/AgeAP.tex}

\bibliography{Bib/bib_bulles.bib}




\end{document}

