\documentclass[11pt]{My_preprint}

\title{
    Buoyancy driven motion of non-coalescing inertial drops: 
    analysis and modeling of the microstructure kinematic with nearest particle statistics. 
}

\author[1,2]{Nicolas Fintzi}
\author[1]{Jean-Lou Pierson}
\author[2]{Stephane Popinet}
\affil[1]{IFP Energies Nouvelles, Rond-point de l’echangeur de Solaize, 69360 Solaize}
\affil[2]{Sorbonne Universit\'e, Institut Jean le Rond d'Alembert, 4 place Jussieu, 75252 PARIS CEDEX 05, France}
\normalmarginpar


\begin{document}

\maketitle

\begin{abstract}
    In this study, we provide a comprehensive analysis of the various  arrangements that droplets can adopt within dispersed buoyant emulsions. 
    This is termed the study of the microstructure.
    To this end, we have developed a novel algorithm capable of effectively prevents numerical coalesce between drops at reasonable computational cost.
    This algorithm is implemented within the Volume of Fluid (VoF) method, utilizing the \href{http://basilisk.fr}{http://basilisk.fr} open source code. 
    Subsequently, we conducted Direct Numerical Simulations (DNS) of statistically steady state mono-disperse buoyant emulsion, over a broad range of \textit{Galileo} number ($Ga$), particle volume fraction ($\phi$), and viscosity ratio ($\lambda$). 
    The density ratio and the \textit{Bond} number are kept constant, $\zeta = 1.11$ and  $Bo = 0.2$, respectively. 
    Then it is shown that, as predicted by \citet{zhang2023evolution}, the second moment of the nearest particle pair distribution, noted \textbf{R}, has the capability to quantify microstructure's features such as clusters and layers of particles.
    In particular, it is found that : 
    (1) At low $Ga$ isotropic clusters appear with increasing $\phi$. 
    (2) Non-isotropic clusters such as layers of particles, are more likely to form for high \textit{Galileo} number.
    (3) The viscosity ratio $\lambda$ has an important impact on the microstructure, clearly more layers are formed for $\lambda = 1$ than $\lambda = 10$. 
    Overall, our study provides a quantitative measure of the microstructure geometry 
     in terms of $Ga$, $\phi$ and $\lambda$. 
\end{abstract}

\section{Introduction}
\input{age/Introduction.tex}

% \input{age/Simulation_Setup.tex}

\section{Theoretical framework}
\label{sec:Theory}
\input{age/The_nearest_particle_statistics.tex}
\input{age/Proof_W.tex}

\section{Numerical methodology}
\label{sec:methodo}
\input{age/Problem_statement.tex}

\section{Results}

\label{sec:results}

\input{age/Time_of_interaction.tex}


\input{age/Velocity.tex}
% \input{age/Velocity2.tex}

\section{Conclusion}
\input{age/conclusion.tex}

\appendix

\section{Numerical validations}
\label{ap:validation}

\input{age/validation.tex}
\input{age/AgeAP.tex}

\bibliography{Bib/bib_bulles.bib}

\end{document}

