%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Define Article %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[
    a4paper,                            % paper format
    12pt,                               % default document font size
    twoside,                            % two sided document to account for binding
    open=right,                         % new chapter open on the right side of the document
    %BCOR=10mm,                          % add a binding correction
    %DIV=14,                             % page layout factor, the larger the factor, the larger the text block.
    %listof=totoc,                       % add list of floats to the table of contents
    %bibliography=totoc,                 % add bibliography to the table of contents
    %numbers=enddot,                     % add dot after chapter/section number
    %headsepline,                        % add heading line separator
    %sfdefaults=false
]{My_book}



\title{Statistical modeling of disperse two-phase flows : application to buoyancy-driven droplets suspensions.}
\author{Fintzi Nicolas}





\usepackage{acro}
\DeclareAcronym{CFD}{short=CFD, long=Computational Fluid Dynamics}
\DeclareAcronym{PBE}{short=PBE, long=Population Balence Equations}

\usepackage[intoc, english]{nomencl}
\makenomenclature


\begin{document}

\dominitoc

\frontmatter
\pagestyle{plain}
\input{parts/titlepage}
\input{parts/abstract}
\input{parts/Acknowledgements}
\input{parts/contents}
\mainmatter



\chapter{General introduction}
\label{part:intro}
% \adjustmtc

\adjustmtc
\minitoc

\input{parts/intro.tex}

\part{Statistical modeling of dispersed two phases flows made of fluids inclusion with interfacial transport}
\label{part:one}

% \etocsettocstyle{}{} % from now on only local tocs
%%%%%%%%%%%%%%%%%%%%%%%%%   CHAPITRE 1
\chapter{Averaged equations for disperse two-phase flow with interfacial transport}
\label{chap:daniel1}
\chapabstract{
    This chapter\footnote{This chapter has been published in \citet{fintzi2024averaged}} provides a derivation of the averaged equations governing the motion of dispersed two-phase flows with interfacial transport. 
    We begin by revisiting the two-fluid formulation, as well as the distributional form of the interfacial transport equation which holds on the entire domain. 
    Following this, a general Lagrangian model is introduced, which accounts for the effects of both internal and interfacial properties of the dispersed inclusions (bubbles, droplets, or particles) within a continuous phase.
    This is achieved by derivation of conservation laws for particle surface and volume-integrated properties. 
    By summing the internal and interfacial conservation laws, we derive a conservation equation for an arbitrary Lagrangian property associated with the inclusion. 
    % The key advantage of this formulation is that the non-convective flux inside the inclusion does not appear in the conservation law. 
    Notably, the non-convective flux inside the inclusion does not appear in the conservation law using this formulation. 
    %We then proceed to derive the the lesser-known conservation equations for the moments related to an arbitrary Lagrangian property.
    We then proceed by deriving the lesser-known conservation equations for the moments of the volume and surface distribution of an arbitrary Lagrangian property.  
    Next, the averaged equations for the dispersed phase are derived through two distinct approaches: the particle-averaged (or Lagrangian) formalism, and the phase-averaged method. 
    The main conclusion of this work is the demonstration of the relation between the particle-averaged and phase-averaged equations. 
    We show that the dispersed phase-averaged equations can be interpreted as a series expansion of the particle-averaged moment equations. 
    The paper concludes by presenting a "hybrid" set of equations, consisting of phase-averaged equations for the continuous fluid phase, complemented by an arbitrary number of moment conservation equations for the dispersed phase.
}
\adjustmtc
\minitoc
\input{The_hybride_model/introduction.tex}
\input{The_hybride_model/Local_scale_laws.tex}
\input{The_hybride_model/Averaged_twofluid.tex}
\input{The_hybride_model/Lagrangian_description.tex}
\input{The_hybride_model/Lagrange_to_euler.tex}
\input{The_hybride_model/Equivalence.tex}
% \input{The_hybride_model/Hybrid_model.tex}
\input{The_hybride_model/Conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%   CHAPITRE 2
\chapter{Averaged equations for Newtonian dispersed two-phase flows with constant surface tension and no interfacial transfer}
\label{chap:daniel15}
\chapabstract{
    % In this chapter we expose the minimal set of equations necessary to describe emulsions made of Newtonian droplets based on the ``hybrid'' formulation developed in the preceding chapter. 
    In this chapter, we derive the ensemble-averaged momentum and energy equations in the ``hybrid'' formalism for arbitrary Newtonian droplets immersed in a Newtonian fluid, including surface tension properties. 
    Notably, this derivation allowed us to discuss the energy exchange present in the mixture. 
    Additionally, we provided an explicit and general formulation for the effective stresses of the emulsion.  
}
\minitoc

\input{The_hybride_model/Ap_hypothesis.tex}
\input{The_hybride_model/fundamental_properties.tex}
\input{The_hybride_model/App_particle_equaitons.tex}
\input{The_hybride_model/App_twofluid_model.tex}
\input{The_hybride_model/App.tex}


%%%%%%%%%%%%%%%%%%%%%%%%% CHAPITRE 4
\chapter{Averaged equations for deformable spheroidal fluid particles}
\label{chap:deformable}
\chapabstract{
In this chapter, we propose to derive an averaged set of equations for deformable droplets. 
It is assumed that the droplet shape remains spheroidal. 
Specifically, we demonstrate how to derive \textit{shape} and orientation equations based on the \textit{moment of momentum} and second \textit{moment of mass} of the particle. 
% This model constitutes the results of the chapter. 
%%%%%%%
% As an application, we propose to evaluate theoretically the effect of droplet deformation on the ensemble-averaged stress of the suspension in the case of uniform relative motion between phases. 
% It is demonstrated that due to the effect of small inertia, the \textit{Stresslet} term present in the effective stress of the continuous phase momentum equation, has a contribution proportional to the mean relative velocity of the dispersed phase. 
% Therefore, uniform relative translation between phases generates effective stresses, which are to be compared to the pseudo turbulence stresses which as we show have the same functional form. 
% In addition, using the particle deformation equation we are able to show that the \textit{Stresslet} term is at the origin of the droplets' deformation. 
% Finally, we give an explicit formula for the droplet deformation based on the particle \textit{Stresslet} in a steady state regime. 
}
\minitoc


\input{Closure_hybrid/introduction.tex}
% \input{Closure_hybrid/Local_scale_laws_simple.tex}
% \input{Closure_hybrid/Lagrangian_description.tex}
\input{Closure_hybrid/Single_Ellipse_4.tex}
\input{Closure_hybrid/Conclusion.tex}   

%%%%%%%%%%%%%%%%%%%%%%% CHAPTER 3
% \chapter{Derivation of the closure problem, and of the closure terms: application to spherical droplets in dilute stokes flow regime. }
\chapter{Derivation of the closure problem for spherical droplets}
\label{chap:daniel2}
\chapabstract{
In this chapter we show how to reformulate any ensemble averaged terms into what we call \textit{single-particle conditional} averaged quantities. 
Doing so, we propose an alternative formulation for partitioning the total momentum exchange term, differing from the one originally proposed by \citet{zhang1997momentum}. 
We then revisit the derivation of (2.10) of \citet{batchelor1972sedimentation} which relates the ensemble-averaged properties of the continuous phase to \textit{single-particle} conditionally averaged quantities.
Notably, we show that the assumptions made by \citet{batchelor1972sedimentation} to derive this formula are not sufficient to get the expression given in his paper.
This explains the convergence issues sometimes encountered when using this relation \citep{batchelor1972sedimentation}. 
To obtain the conditional averaged quantities, we follow \citet{hinch1977averaged}, and we propose a generic routine to derive the \textit{single-particle conditional averaged} Navier-Stokes equations. 
We show that in the limiting case of low volume fraction, we find back the classic equations of an isolated droplet immersed in an unbounded fluid. 
% Additionally, we discuss that our method can be extended to more complicated situations, which might lead to the consideration of inertia, non-vanishing volume fraction of droplets, or gradient of concentration for example.
%%%%%%%%%%%%%% a mettre dans lautre cahpitre 
% Then, we derive the closure terms of the hybrid models accurate at $\mathcal{O}(\phi)$ for spherical droplets in Stokes flows.
% While many of these were already established, we introduced several new closures, especially for the pseudo-turbulent energy equation.  
} 
\minitoc
\input{The_hybride_model/The_closure_poblem.tex}





% \input{parts/part3_intro}
% \input{parts/part3s1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% PART 2 %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\part{Closure terms modeling for mono-disperse buoyant emulsions of nearly spherical droplets}
\label{part:two}





\chapter{Getting the closure terms with Direct Numerical Simulations (DNS)}
\label{chap:DNS}
\chapabstract{
    In the perspective of developing closure laws, we now present the numerical experiment setup\footnote{Some of the results in this chapter have been published in \citet{fintzi2024buoyancy}}.
    We use the open source code \href{http://basilisk.fr}{http://basilisk.fr} to model mono-dispersed buoyant emulsions. 
    Particularly, we introduce an algorithm that prevents numerical coalescence in DNS of droplets emulsion, while maintaining a reasonable computational cost. 
    It is termed the \texttt{no-coalescence} algorithm, it has been developed in major part during the PhD. of \citet{mani2021numerical}. 
    This algorithm is integrated into the Volume of Fluid (VoF) method and implemented using the open-source code \href{http://basilisk.fr}{http://basilisk.fr}. 
    Finally, we present some additional work that has been implemented into the Basilisk C precompiler. 
}
\minitoc

% \input{microstructure/Problem_statement.tex}
\input{microstructure/Problem_statementbis.tex}
\input{microstructure/Simulation_Setup.tex}
\input{microstructure/no_coalesence.tex}
\input{parts/einstein_sum.tex}
\input{microstructure/Conclusionbis.tex}


\chapter{Closure in viscous dominated flows}
\label{chap:closure-disperse}
\chapabstract{    
    In this chapter, we derive the closure terms of the hybrid model accurate at $\mathcal{O}(\phi)$ for spherical droplets in Stokes flows.
    While many of these were already established, we introduced several new closures, especially for the pseudo-turbulent energy equation.  
    Then, following the work of \ref{chap:deformable} we propose to evaluate the effect of droplet deformation on the ensemble-averaged stress of the suspension in the case of uniform relative motion between phases. 
    It is demonstrated that due to the effect of small inertia, the \textit{Stresslet}  term present in the effective stress of the continuous phase momentum equation, has a contribution proportional to the mean relative velocity of the phases. 
    Consequently, uniform relative translation between phases generates effective stresses through the \textit{Stresslet} term. 
    This contribution is compared to the \textit{Reynolds} stress which as we show have the same magnitude in the moderately dense regime ($\phi =0.2$). 
    In addition, using the droplet deformation equation \eqref{chap:deformable} we give an explicit expression for the droplet deformation tensor in the steady state regime. 
    Both, the \textit{Stresslet} term and deformation tensor are compared to the numerical results, good agreements are obtained. 
}
\minitoc

\input{The_hybride_model/closure_stokes_spherical.tex}
\input{Closure_hybrid/Ellipsoid_4.tex}


\chapter{Yet another drag force correlation}
\label{chap:mono-disperse}
\chapabstract{    
    % In this brief study, we propose a new model for the interphase drag force term to be used in the averaged Navier-Stokes equations. 
    % This model is restricted to homogeneous and steady-state, mono-disperse multiphase flows. 
    Drawing upon previous numerical and experimental studies in the literature, we develop a drag force model that accounts for arbitrary viscosity ratios between the dispersed and continuous phase, noted $\lambda$. 
    Most prior models have focused on sedimentation involving solid particles or buoyant rising bubbles. 
    Following \citet{rivkind1976flow}, we interpolate between these two classes of models to create a robust formulation that remains valid for intermediate values of $\lambda$, across all Reynolds numbers $Re$ and volume fractions $\phi$.
    Specifically, we employ the models of \citet{schiller1933} and \citet{mei1994} to describe the drag force on solid spheres and spherical bubbles, respectively.
    We then incorporate a Richardson-Zaki law made for solid particles to account for the volume fraction ($\phi$), at arbitrary \textit{Reynolds} numbers ($Re$) \citep{kramer2019improvement}.
    To account for the variable $\lambda$, we adjust the Richardson-Zaki exponent based on experimental observations in the Stokes regime \citep{ishii1979drag}. 
    The \texttt{no-coalesence.h} algorithm presented in our previous study enables us to perform statistically steady-state simulations of mono-disperse buoyant droplets for various \textit{Galileo} numbers $Ga = 5 \rightarrow 10$, volume fractions $\phi =1\% \rightarrow 20\%$ and viscosity ratios $\lambda = 0.1,1,10$. 
    From these DNS simulations, we could measure the drag coefficient and compare it to the semi-empirical prediction developed in this study. 
    By comparing our literature-based model with DNS results, we successfully validate this new drag force coefficient in the intermediate $\lambda$ regime.
}
\minitoc


\input{Pseudo_turb/Introduction.tex}
\input{Pseudo_turb/closure.tex}
\input{Pseudo_turb/rising_velocity.tex}
\input{Pseudo_turb/Conclusion.tex}


\chapter{Pseudoturbulence in a mono disperse suspension of rising droplets}
\label{chap:pseudoturbulence}
\chapabstract{
    In this chapter we derive an analytical expression for the continuous phase \textit{Reynolds stress} tensor. 
    This derivation is restricted to the dilute regime where the dispersed phase volume fraction labeled $\phi$ is vanishingly small and for droplet Reynolds number $Re \ll 1$. 
    % In this context we derive an analytical formula for the pseudoturbulence generated by translating bubbles or droplets inside a Newtonian fluid. 
    To by-pass the integral convergence difficulties generated due to the $\mathcal{O}(r^{-1})$ decay of the disturbance velocity field \citep{caflisch1985variance}, we make use of the Nearest-Particle-Statistical (NPS) as it is introduced in \citet{zhang2021ensemble}. 
    Good agreements are obtained between this model and experimental results from the literature \citep{cartellier2009induced}.  
    Then, based on the DNS results \eqref{chap:DNS} and findings from the literature, we propose an extension of this model up to $\phi = 0.2$ and $Re = 100$. 
}
\minitoc

\input{On_pseudo_turbulence/Introduction.tex}
\input{On_pseudo_turbulence/Classic_pair_stat.tex}
\input{On_pseudo_turbulence/Nearest_stats.tex}
\input{On_pseudo_turbulence/Numerical_results.tex}
\input{On_pseudo_turbulence/Conclusion.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% PART 3 %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \part{Buoyancy driven motion of non-coalescing inertial drops}
\part{Nearest particle statistics: Analysis and modeling of the microstructure geometry and kinematics, in buoyant emulsion of nearly spherical droplets}
\label{part:three}



\chapter{Microstructure modeling with nearest particle statistics}
\label{chap:microstructure}
\chapabstract{
    In this study\footnote{This chapter has been published in \citet{fintzi2024buoyancy}}, we analyze the various arrangements that droplets can form within dispersed buoyant emulsions, which we refer to as the study of microstructure. 
    % To this end, we have developed a novel algorithm that effectively prevents numerical coalescence between drops while maintaining a reasonable computational cost. 
    % This algorithm is integrated into the Volume of Fluid (VoF) method and implemented using the open-source code \href{http://basilisk.fr}{http://basilisk.fr}. 
    % We perform Direct Numerical Simulations (DNS) of statistically steady state mono-disperse buoyant emulsion over a broad range of dimensionless parameters, including the droplet volume fraction ($\phi$), the Galileo number ($Ga$) and the viscosity ratio ($\lambda$). 
    We make use of nearest particle statistics to quantify the microstructure properties.  
    As predicted by \citet{zhang2023evolution}, it is demonstrated that the second moment of the nearest particle pair distribution can effectively quantify microstructural features such as droplet clusters and layers. 
    Specifically, the findings are: (1) In moderately inertial flows ($Ga=10$), droplets form isotropic clusters. 
    In high inertial regimes ($Ga=100$), non-isotropic clusters, such as horizontal layers, are more likely to form. 
    (3) The viscosity ratio plays a significant role in determining the microstructure, with droplets that are less viscous or equally viscous as the surrounding fluid tending to form layers preferentially. 
    Overall, our study provides a quantitative measure of the microstructure 
     in terms of $Ga$, $\phi$ and $\lambda$.  
}
\minitoc

% \input{microstructure/Introduction.tex}
\input{microstructure/Introductionbis.tex}

% \input{microstructure/Simulation_Setup.tex}
% \input{microstructure/no_coalesence.tex}
% \input{parts/einstein_sum.tex}

% \input{microstructure/Problem_statement.tex}
\input{microstructure/Problem_statementter.tex}
\input{microstructure/The_nearest_particle_statistics.tex}
\input{microstructure/Non_Inertial.tex}
\input{microstructure/Inertial.tex}
\input{microstructure/Conclusionter.tex}


\chapter{Analysis and modeling of the microstructure kinematics}
\label{chap:microstructure_kin}
\chapabstract{
In this study, we provide a comprehensive analysis of the timescales that govern the droplets' interaction as well as the global microstructure in buoyant emulsions. 
It is shown in (\citet{fintzi2024buoyancy} and \ref{chap:microstructure}) that as predicted by \citet{zhang2023evolution}, the second moment of the nearest particle pair distribution, noted \textbf{R}, can quantify microstructure features such as clusters and layers of droplets.
In this study, we propose to analyze the microstructure kinematics through the derivation of a transport equation for \textbf{R}.  
% We conducted Direct Numerical Simulations (DNS) of statistically steady state mono-disperse buoyant emulsions, over a broad range of \textit{Galileo} numbers ($Ga$), droplet volume fractions ($\phi$), and viscosity ratios ($\lambda$). 
% The density ratio and the \textit{Bond} number are kept constant, $\zeta = 1.11$ and  $Bo = 0.2$, respectively. 
By a rigorous theoretical and numerical analysis we show that :
(1) the time of relaxation of $\textbf{R}(\textbf{x},t)$, is the mean time of interaction of the  nearest droplets pairs $\tau_p(\textbf{x},t)$;
(2) The droplet normal approach velocity scale as $\tau_p n_p^{1/3}$ with $n_p$ the number density, and has also a relaxation time of $\tau_p$.
(3) We evaluate the different source terms in the transport equation for $\textbf{R}$ in terms of the dimensionless parameters. 
Overall the mean time of interaction $\tau_p$ seems to be a crucial quantity in the modeling of the relative kinematics   of droplets in dispersed two-phase flows.
This is particularly useful for the modeling of collision or coalescence kernels, as these quantities involve the mean normal approach velocity between droplets. 
}
\minitoc


\input{age/Introduction.tex}
\input{age/The_nearest_particle_statistics.tex}
\input{age/Proof_W.tex}
\input{age/Problem_statement.tex}
\input{age/Time_of_interaction.tex}
\input{age/Velocity.tex}
% \input{age/Velocity2.tex}
\input{age/Conclusion.tex}




% \section{The Reynolds stress}
% \input{Pseudo_turb/Reynolds_stress.tex}

%################## CHPTER ON PSEUDO TURB 


\part*{Conclusion and Perspectives}
\addcontentsline{toc}{part}{Conclusion and perspectives}


\chapter*{Conclusion}
\input{parts/part5s1}



\appendix
% \appendix
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\Alph{section}.\arabic{subsection}}
\part*{Appendix}
\addcontentsline{toc}{part}{Appendix }

\input{The_hybride_model/Velocity_definition.tex}
\input{The_hybride_model/Arbitrary_moments_eq.tex}
\input{The_hybride_model/taylor_exp.tex}
\input{The_hybride_model/Arbitrary_moments_equivalence.tex}
\input{The_hybride_model/Bulk_stress.tex}


% \input{Appendix/Averaging}
% \input{Appendix/Equivalence}
% \input{Appendix/cinematique}
% \input{Appendix/Shape}
% \input{Appendix/Exp}
% \input{Appendix/distrib}
\input{Closure_hybrid/Single_Ellipse_3.tex}
\input{Closure_hybrid/Surface_tension.tex}
\input{Closure_hybrid/Avg_eq_deformable.tex}

\input{The_hybride_model/A_droplet_in_shear_flow.tex}
\input{Closure_hybrid/reciprocal_theorem.tex}

\input{microstructure/AgeAP.tex}
\input{microstructure/validation.tex}

\input{age/validation.tex}
\input{age/AgeAP.tex}

\input{Pseudo_turb/Appendix1.tex}


\section{
Discussion on the bulk averaged formulation, for the modeling of dispersed multiphase flows made of incompressible fluids
}
\label{ap:momentum_formulation}
% \chapabstract{
%     To conclude this manuscript we would like to present what we think is the simplest way to solve the averaged equations for a mixture of two incompressible fluids.
%     In the first place we present the ``single-phase-like'' mixture equations, which according to me is the most efficient way to solve the mixture equations since it can use a single phase solver. 
%     Then we incorporate the closure terms presented in this manuscript, inside this system of equation, and present a first glimpse of the methodology to solve numerically the latter equations.
%     Overall the perspective of this novel methodology seem very efficient and simplify greatly the multiphase flow problem.  
% }
% \minitoc

\input{EulerEuler/Incompressible_formulation.tex}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{Bib/bib_bulles.bib}


\end{document}
