\documentclass[12pt]{My_preprint}
\title{
    Rheology of dilute suspensions made of slightly inertial buoyant spherical droplets. 
    }

\author[1,2]{Nicolas Fintzi and  Jean-Lou Pierson}

\normalmarginpar


\begin{document}

\maketitle

\begin{abstract}
    In \citet{lhuillier1996contribution} it is shown that the averaged first moment (Stresslet), and second moment, of the hydrodynamic forces on the dispersed phase, govern the rheology of suspensions, whether it is through an effective viscosity or more complex rheological behaviours. 
    In this work, we compute the first and second moments of forces acting on a translating spherical droplet immersed in a uniform flow. 
    In opposition to existing studies, we consider a low but finite Reynolds number, $Re =a u_r \rho_f/\mu_f$, based on the relative velocity $u_r$ and the droplet radius $a$, with $\rho_f$ the density and $\mu_f$ the viscosity of the continuous phase. 
    The $O(Re)$ correction to the drag force is the Oseen contribution, which scales as $O(a^2 u_r^2 \rho_f$). 
    It is shown here that the $O(Re)$ correction to the first and second moments of forces scale as $O(a^3 u_r^2 \rho_f)$ and $O( a^4 \rho_f u_r^2)$, respectively. 
    % Here, $u_r$ is the relative velocity between the droplet and the averaged flow of the mixture, $\rho_f$ the density of the continuous phase, and $a$ the droplet radius.
    Because these moments are proportional to the square of the droplet velocity, averaging over all configurations introduces an additional term proportional to the variance of the droplet center of mass velocity. 
    The main result of the paper is that: in a dilute emulsion of buoyant droplets, the effective stress is proportional to the square of the relative motion between the phases and to the velocity variance of the dispersed phase, and to the gradients of these quantities.
    At this stage the Reynolds stress and particle velocity variance were not computed explicitly, hence this study remains incomplete.
    Finally we demonstrate how to compute the deformation of a translating droplet using the Stresslet tensor.
    The result yields identical to \citet{taylor1964deformation}'s formula but in tensor form. 
\end{abstract}


\input{Stress_in_translation/Secontion_1.tex}
\input{Stress_in_translation/reciprocal_theorem2_2.tex}
\input{Stress_in_translation/deformation.tex}
\input{Stress_in_translation/rheology.tex}
\input{Stress_in_translation/conclusion.tex}



\section*{Acknowledgment}

The author thanks H. Stone for shearing his work with us \citep{stone2001inertial} which largely inspired the methodology and presentation of this paper. 


\bibliography{Bib/bib_bulles.bib}
\appendix
\input{Stress_in_translation/second_mom.tex}
\input{Stress_in_translation/negligible_otter.tex}

\end{document}

