\documentclass[11pt]{My_preprint}


\title{Averaged equations for disperse two-phase flow with interfacial transport}

\author[1,2]{Nicolas Fintzi}
\author[2]{Daniel Lhuillier}
\author[1]{Jean-Lou Pierson}
% \author[2]{Stephane Popinet}
\affil[1]{IFP Energies Nouvelles, Rond-point de l’changeur de Solaize, 69360 Solaize}
\affil[2]{Sorbonne Université, Institut Jean le Rond $\partial$’Alembert, 4 place Jussieu, 75252 PARIS CEDEX 05, France}

\begin{document}

\maketitle

\begin{abstract}
    This article presents a comprehensive study of the averaged equations two-phase flow with interfacial transport.
    We present a systematic derivation of a general averaged hybrid model that incorporates the influence of internal properties and surface properties of arbitrary particles dispersed in a continuous phase.
    The dispersed phase averaged equations are derived using two distinct formalism :
    the particle-average or Lagrangian formalism proposed by \citet{zhang1994ensemble,jackson1997locally};
    and the phase-average method, which is also employed for the continuous phase based on the approach of \citet{drew1983mathematical}. 
    The particle-phase averaged formalism yields the conventional linear conservation equations, as well as the less familiar moments' conservation equations.
    The primary contribution of this work is the demonstration of the equivalence between the particle-averaged and phase-averaged equations. 
    We show that the dispersed phase-averaged equation, is in fact a series expansion of the so-called particle-averaged moments equations. 
    The second contribution of this work is the derivation of the arbirary order moment equations of the particle phase in their most generalized form. 
    The ambition of the manuscript is to provide a set of equation adaptable to any kind of dispersed two phase flow and discuss the various form it can take depending on the particle nature. 
\end{abstract}

%In this work we provided a well-developed hybrid model for dispersed two phase flow made of fluid particles.
%The main contribution of the work is the derivation of a generalized formulation of what is called a \textit{Hybrid model} for dispersed two phase flows. 
%This model it is derived in the most general way incorporating volume and surface property of the particles.

%After averaging the equations that govern the dispersed phase using two distinct frameworks, namely, the phase-average and the particle-average, we demonstrated the equivalence between both formalism. 
%In light of \ref{eq:scheme_equivalence} we reached the major conclusion of this work, i.e.  the phase-averaged equation for the dispersed phase, is a series expansion of the particle-averaged equations.  
%As expected by several authors \citep{zhang1997momentum,nott2011suspension} it is therefore possible to describe a particle with an arbitrary order of accuracy by using the moments equations of a particle. 
%In this work we provided the general form of these equations together with a clear physical explanation of the moment equations. 
%This statement is only true if one assume that the Taylor series used in the process are convergent within the particles domains. 

% Acknowledging this fact we concluded that  any physical phenomenon could be modeled with the moments equations since they constitute the phase-averaged equation, i.e. \ref{eq:avg_dt_chi_f} with $k =2$. 
%The final system of equation, from \ref{eq:avg_hybrid_dt_chi_f} to \ref{eq:avg_hybrid_q_1} is constituted of a conservation equation for the continuous phase averaged quantity $f_f$, and $n$ dispersed phase equations for the moments $\textbf{q}_p^{(n)}$. 
%The equations for the moments $\textbf{q}_p^{(n)}$ posses each a well-defined physical sense that are related to the moment of the distribution of the local quantity $\chi_df_d^0 + \delta_\Gamma f_\Gamma^0$ inside the particles. 
%Then, we clarified the role of the non-convective fluxes on the dispersed phase properties. 

%Overall, the main advancement of this model is its ability to incorporate the effects of the particles' surface properties within the Lagrangian balance laws of arbitrary order, and provides a framework for deriving particle-average equations tailored to any type of problem.


\input{The_hybride_model/introduction.tex}

\section{The two-fluid formulation}
\label{sec:two-fluid}
\input{The_hybride_model/Local_scale_laws.tex}
\input{The_hybride_model/Averaged_twofluid.tex}

\section{Lagrangian equations for the dispersed phase}
\label{sec:Lagrangian}
\input{The_hybride_model/Lagrangian_description.tex}


%\section{The hybrid model}
\section{The ``hybrid'' description of the two phases}
\label{sec:averaged_eq}
\input{The_hybride_model/Lagrange_to_euler.tex}
\input{The_hybride_model/Equivalence.tex}
% \input{The_hybride_model/Hybrid_model.tex}

% \section{Mass, momentum and total energy}
% \label{ap:hypothesis}
% \input{The_hybride_model/Ap_hypothesis.tex}
% \input{The_hybride_model/fundamental_properties.tex}
% \input{The_hybride_model/App_particle_equaitons.tex}
% \input{The_hybride_model/App_twofluid_model.tex}
% \input{The_hybride_model/Bulk_stress.tex}

% \section{Application}
% \label{sec:application}
% \input{The_hybride_model/App.tex}
% \input{The_hybride_model/Continuous_phase_stress.tex}

\section{Discussion}
\input{The_hybride_model/Conclusion.tex}
%\input{Closure_hybrid/Disscusion.tex}



\section*{Acknowledgement}
It is a great pleasure to dedicate this paper to Daniel Lhuillier whose work on the "hybrid formalism" has greatly influenced the vision of both co-authors and the present work. 
As a scientist, Daniel Lhuillier serves as a mentor for young researchers. 
He constantly challenges us to question the significance and novelty of our findings and encourages us to explore papers that the authors may have overlooked.
His constant guidance have also been a source of motivation to complete this work.
The authors are also grateful for many in-depth discussions with Professor St\'ephane Popinet as well. 

%We would like to express our sincere gratitude to Professor D. Lhuillier for his inspiring and insightful classes, which has greatly influenced our work.
%Also, the authors are grateful for many in-depth discussions with Professor St\'ephane Popinet from \textit{Institut Jean le Rond Alembert} as well. 

\section*{Data availability}

The python script used to derive analytically the closures are available upon request to the authors. 


\appendix

\input{The_hybride_model/Velocity_definition.tex}
\input{The_hybride_model/Arbitrary_moments_eq.tex}
% \input{The_hybride_model/conditional_eq_notes.tex}
% \input{The_hybride_model/The_closure_poblem.tex}
% \input{The_hybride_model/A_droplet_in_shear_flow.tex}

\bibliography{Bib/bib_bulles.bib}
\end{document}
