In this section we expose the strategy employed to conduct statistically steady state simulations of rising mono-disperse suspension of droplets in a fully periodic domain. 
We start by introducing the physical parameter, followed by a description of the numerical methods.
Lastly, we detail the methodology adopted to collect statistics about microstructure, which are presented in the next sections.

The source code used to perform the DNS is entirely open source.
The simulations are running within the \texttt{Basilisk C} framework, (see \href{http://basilisk.fr}{basilisk.fr}), which is an extension of the C programming language, adapted for the solution of partial differential equations on Cartesian meshes. 
Note that this section is complemented by the wiki page, \href{http://basilisk.fr/sandbox/fintzin/Rising-Suspension/RS.c}{RS.c}, where the reader can access the source code used to conduct the DNS, as well as comments and notes to help comprehension. 

\subsection{Problem statement}

We investigate numerically the dynamics of homogeneous mono-disperse emulsions subject to buoyancy forces in a fully periodic domain. 
Both the dispersed and continuous phase are considered as Newtonian fluids defined by viscosity $\mu_d$ (resp. $\mu_f$) and density $\rho_d$ (resp. $\mu_f$).
Throughout this work, the subscript $_d$ and $_f$ indicate properties belonging to the dispersed and continuous phase respectively. 
The interface between both fluids is considered as infinitely thin and deprived of any impurities and a constant surface tension with a coefficient $\gamma$ is assumed. 
The density and viscosity will be considered constant in each phase.
In dimensionless form this problem is completely characterized by six dimensionless parameters :  the viscosity and density ratio, $\lambda = \mu_d / \mu_f$ and $\zeta = \rho_d / \rho_f$,  
the \textit{Galileo} number, 
\begin{equation*}
    Ga =\sqrt{\rho_f(\rho_f - \rho_d) g d^3} / \mu_f,
\end{equation*}
the \textit{Bond} number, 
\begin{equation*}
    Bo =\frac{(\rho_f - \rho_d) g d^2}{\gamma},
\end{equation*}
the number of droplets per domain $N_b$, and the dispersed phase volume fraction $\phi$. 
Here, $d$ represents the diameter of a sphere with the same volume as the droplets, and $g$ denotes the gravitational acceleration.
The \textit{Galileo} number is a measure of the strength of the buoyancy forces relative to the viscous forces, whereas the \textit{Bond} number evaluates the ratio between buoyancy and capillary forces. 

To provide a brief overview of the range of interest for these numbers in an industrial context, let us consider the example of a vegetable oil/water system.
In most liquid-liquid system encountered in industrial processes the diameter of the droplets lies in the range $d = [50 \mu \text{m}, 3 \text{mm}]$.
The density and viscosity of water are approximately $\rho_f = 1000 \text{kg/m}^3$ and $\mu_f = 10^{-3} \text{Pa.s}$, respectively.
The density and viscosity of oil are close to $\rho_d = 900 \text{kg/m}^3$ and $\mu_d = 10^{-2} \text{Pa.s}$, respectively.
We consider the gravitational acceleration on earth, thus $g= 9.81 \text{m.s}^{-2}$.
The surface tension of the oil/water system is approximately $\sigma = 0.05 \text{N/m}^2$ \citep{de2015gouttes}. 
\begin{table}[h!]
    \centering
    \caption{Dimensionless parameters of a water/oil system.}
    \begin{tabular}{|c||c|c|c|c|c|}
        \hline&$Ga$&$Bo$&$\phi$&$\lambda$&$\zeta$\\ \hline
        \hline Oil/Water&$[0.35,160]$&$[10^{-5};10^{-1}]$&$<0.2$&$10$&$0.9$\\ \hline
    \end{tabular}
    \label{tab:parameters_exp}
\end{table}
\ref{tab:parameters_exp} gives the corresponding dimensionless parameters.  
Notice that the \textit{Bond number} is relatively low, indicating that the droplets are nearly spherical in these processes.
Additionally, the maximum volume fraction is set to $\phi = 0.2$, indeed above such $\phi$ particles coalesce easily and the topology of the flow cannot be considered as dispersed anymore. 


Following \ref{tab:parameters_exp}, to approach real-life applications we conducted DNS for four volume fractions, specifically $\phi = 0.01,0.05,0.1,0.2$.
In contrast to most of the previous studies, we choose to keep the number of droplets constant while changing the volume fraction $\phi$. 
We then modify the domain size $\mathcal{L}$ accordingly. 
This introduces another dimensionless parameter of interest : $\mathcal{L}/d$, which measures the confinement of the particles within the finite numerical domain. 
This parameter is purely determined by $\phi$ and $N_b$, and will thus be refereed as a \textit{secondary parameter}.

As mentioned, the \textit{Bond} numbers of our targeted application is very low.
Therefore, and it will stay constant throughout this study, the \textit{Bond} number is set to $Bo = 0.2$.
DNS with lower \textit{Bond} numbers become excessively expensive due to the restrictive capillary time step constraint. 
However, we assert that for $Bo \leq 0.2$ the droplet shape essentially remains spherical at least for small \textit{Galileo} numbers. 
Additionally, the ratio between inertia and surface tension forces is given by the \textit{Weber} number, 
\begin{equation*}
    We = \frac{Bo \cdot Re^2}{Ga},
\end{equation*}
where $Re = \frac{\rho_f d U}{\mu_f}$ is the Reynolds number based on the phase drift velocity $U$.
Values of \textit{Reynolds} numbers for each DNS are provided in \ref{ap:age} \ref{fig:Reall}. 
Extreme values of $We$ reached in these simulations are displayed in \ref{tab:simulations}. 
It is clear that for $We=0.6$ we might expect some deformations, nevertheless, for most of the cases $We$ stays below these values. 
Consequently, whether it is in the viscous regime or inertial regime, the droplets are expected to remain spherical according to the values of $Bo$ and $We$.
This statement will be verified in \ref{sec:microstructure}. 

Density and viscosity ratio of droplets in real life applications are reported in \citet[Figure 1.]{balla2020effect}.
As depicted in \citet[Figure 1.]{balla2020effect}, the viscosity and density ratio of fluid-fluid systems range between, $\lambda \in [10^{-4} : 10^4]$ and $\zeta \in [10^{-1} : 10^1]$, respectively. 
In this study we restrict our attention to a single density ratio, $\zeta = 0.9$.
Regarding the viscosity ratio, we accomplished DNS for 2 different values, namely $\lambda = 1,10$.
Lastly, to explore the effect of inertia on the microstructure, the \textit{Galileo} number will vary within the range $Ga \in [5,100]$.

The primary objective of the study is to investigate the microstructure through the nearest particle pair distribution function.
Thus it is crucial to obtain a sufficient number of DNS samples to ensure statistical convergence. 
Also, the physical quantities measured in these DNS must remain independent of the domain size. 
Therefore, we use a number of particles per domain of $N_b = 125$, which is roughly what \citet{hidman2023assessing} used for their DNS of fully-periodic buoyant rising bubbles.
Moreover, each DNS lasts for a time : $t^*_\text{end} = 1500 \sqrt{d/g}$.
% It is shown in \ref{ap:validation} that these parameters  are sufficient to obtain well converged statistics.  
\begin{table}[h!]
    \centering
    \caption{Dimensionless parameter range investigated in this work.}
    \begin{tabular}{|ccccccc|ccc|}\hline
        \multicolumn{7}{|c|}{Primary parameters}&\multicolumn{3}{|c|}{Secondary parameters}\\\hline\hline
        $Ga$&$Bo$&$\phi$&$\lambda$&$\zeta$&$N_b$&$t^*_\text{end}$&$\mathcal{L}/d$&$Re$&$We$\\ \hline
        $5\rightarrow 100$&$0.2$&$1\% \rightarrow 20\%$&$10$ \& $1$&$0.9$&$125$&$1500$&$6.7\to 18.7$&$10^{-1}\to 170$&$10^{-4}\to 0.6$\\ \hline
    \end{tabular}
    \label{tab:simulations}
\end{table}
In this study we present DNS results with dimensionless parameters lying in ranges outlined in \ref{tab:simulations}.
In summary, we investigated $5$ \textit{Galileo} number $Ga = 5,10,25,50,100$, $4$ different volume fractions $\phi = 0.01,0.05,0.1,0.2$, and two viscosity ratios $\lambda =1,10$ with $Bo = 0.2$ and $\zeta = 0.9$. 
This makes a total of $40$ representative simulations of $N_b = 125$ droplets which last for $t= 1500 \sqrt{d/g}$. 
