
The DNS results presented in this study are based on the exact same set of data than our previous work \citet{fintzi2024buoyancy}, were we conducted statistically steady-state simulations of rising mono-disperse suspensions of droplets in a fully periodic domain. 
This section is only summary of the numerical methods presented in \citet{fintzi2024buoyancy}, with additional information regarding the computation of statistics employed here. 
Note that the source code of the DNS and the post processes tools used in this section are provided and documented on the wiki page : \href{http://basilisk.fr/sandbox/fintzin/Rising-suspension/RS.c}{RS.c}. 



\subsection{Problem statement and numerical methods}


We consider the dynamics of homogeneous mono-disperse emulsions subject to buoyancy forces in a fully periodic domain. 
Both the dispersed and continuous phase are considered as Newtonian fluids defined by viscosity $\mu_d$ (resp. $\mu_f$) and density $\rho_d$ (resp. $\mu_f$).
The interface between both fluids is modeled with a constant surface tension coefficient, $\gamma$. 
Equally, the density and viscosity will be considered constant in each phase.
In dimensionless form this problem is completely characterized by six dimensionless parameters :  the viscosity and density ratio, $\lambda = \mu_d / \mu_f$ and $\zeta = \rho_d / \rho_f$,  
the \textit{Galileo} number, 
\begin{equation*}
    Ga =\sqrt{\rho_f(\rho_f - \rho_d) g d^3} / \mu_f,
\end{equation*}
the \textit{Bond} number, 
\begin{equation*}
    Bo =\frac{(\rho_f - \rho_d) g d^2}{\gamma},
\end{equation*}
the number of droplets per domain $N_b$, and the dispersed phase volume fraction $\phi$. 
Here, $d$ represents the diameter of a sphere with the same volume as the droplets, and $g$ denotes the gravitational acceleration.
The \textit{Galileo} number is a measure of the strength of the buoyancy forces relative to the viscous forces, whereas the \textit{Bond} number evaluates the ratio between buoyancy and capillary forces. 
We used a number of particles per domain of $N_b = 125$, which is roughly what \citet{hidman2023assessing} used for their DNS of fully-periodic buoyant rising bubbles.
Moreover, each DNS lasts for a time : $t^*_\text{end} = 1500 \sqrt{d/g}$.
These parameters are sufficient for to obtain a goo statistical convergence \citet{fintzi2024buoyancy}. 
\begin{table}[h!]
    \centering
    \caption{Dimensionless parameter range investigated in this work.}
    \begin{tabular}{|ccccccc|ccc|}\hline
        \multicolumn{7}{|c|}{Primary parameters}&\multicolumn{3}{|c|}{Secondary parameters}\\\hline\hline
        $Ga$&$Bo$&$\phi$&$\lambda$&$\zeta$&$N_b$&$t^*_\text{end}$&$\mathcal{L}/d$&$Re$&$We$\\ \hline
        $5\rightarrow 100$&$0.2$&$1\% \rightarrow 20\%$&$10$ \& $1$&$0.9$&$125$&$1500$&$6.7\to 18.7$&$10^{-1}\to 170$&$10^{-4}\to 0.6$\\ \hline
    \end{tabular}
    \label{tab:simulations}
\end{table}
In short, we present DNS with dimensionless parameters lying in ranges outlined in \ref{tab:simulations}.

The governing equations describe the motion of two immiscible fluids of different densities and viscosities separated by an interface with surface tension. 
We use the so-called ``one fluid'' formulation of the variable density and viscosity Navier-Stokes equations, which can be expressed as 
\begin{align}
    \pddt \rho+ \div(\rho\textbf{u})
    &= 0,\\
    \label{eq:dt_urho}
    \pddt (\rho \textbf{u})
    + \div (\rho  \textbf{u} \textbf{u} - \bm\sigma)
    &= (\avg{\rho} - \rho)\textbf{g}
    + \textbf{f}_\gamma,\\
    \label{eq:dt_C}
    \pddt C + \textbf{u}\cdot\grad C  
    &= 0,
\end{align}
i.e. the mass, momentum and colors function transport equations, respectively. 
The scalar fields $C$, represents the color function, which ranges between $0$ and $1$ to indicate the volumetric proportion of each phase.
We introduced the fluid velocity vector $\textbf{u}$ and the Newtonian stress tensor $\bm{\sigma} = -p \textbf{I} + \mu (\grad \textbf{u}+ \grad \textbf{u}^\dagger)$ where $p$ is the pressure field and $^\dagger$ represents the transpose operator.
Note that the material properties, $\rho$ and $\mu$, take the values of each phase in presence, using the arithmetic average : $\rho = (1-C)\rho_f + C \rho_d$ and $\mu = (1-C)\mu_f + C \mu_d$. 
The capillary force is defined as, $\textbf{f}_\gamma =\textbf{n} \gamma \div \textbf{n} $, where \textbf{n} is the normal to the interface.
Following  \citep{bunner2002dynamics}, we incorporated the artificial body force term, $\avg{\rho}\textbf{g}$, on the right-hand side of \ref{eq:dt_urho}, to maintain a zero-averaged velocity throughout the entire numerical domain.  

To solve these equations we first initialized $125$ spherical droplets within a cubic domain with fully periodic boundary condition. 
We used the open source code \url{http///basilisk.fr} to discretize the governing equations. 
Additionally, we used a novel algorithm (discussed in detail in \citep{mani2021numerical,fintzi2024buoyancy}) to prevents coalescence between droplets so that we preserve a mono-disperse population of droplets. 
This algorithm is based on the Mult-VoF methodology. 
The key principle is to use different VoF tracers for adjacent droplets, but allow several non-touching droplets to be in the same VoF tracer.
This algorithm is shown to preserve the kinematic behavior of interfaces which are in close contact, even thought we do not resolve the thin liquid film between them \citep{fintzi2024buoyancy}. 
Note that this is of major importance since this study focuses on the relative velocity of droplets in interaction. 

\subsection{Numerical sampling and statistical convergence}

The age-included nearest-neighbor distribution function presented in the last section requires the particles' center of mass position and the position of its nearest neighbor, along with the current age of interaction.
Equally, the center of mass velocity of the particles together with the velocity of their nearest neighbor is also needed to reconstruct $\textbf{w}_p^{nst}$. 
Even though these quantities are basic, they are not evident to measure in DNS.
Indeed, when several droplets belong to the same VoF tracer it is challenging to distinguish them.
Therefore, some comments are in order.   

As detailed in \citet{fintzi2024buoyancy} the \href{http://basilisk.fr/src/tag.h}{tag.h} algorithm permits us to distinguish the different droplet volumes within a given VoF field. 
Let define $\texttt{t}_i[\text{c},t]$ as the ``tag'' field corresponding to the droplet $i$, evaluated at the cell ``c'' of the mesh and at time $t$.
This field is equal to 1 for cells inside the volume of the particle $i$ and 0 outside.
Then, the \href{http://basilisk.fr/src/tag.h}{tag.h} algorithm provides us with $N$ ``tag'' field, i.e. one for each droplet. 
Based on $\texttt{t}_i$, and on the other fields solved by \ref{eq:dt_C} and \ref{eq:dt_urho}, we can easily define the particles Lagrangian properties mentioned above. 
The mass, position and momentum of a particle are then computed as follows 
\begin{align*}
    m_i(t)
    = \sum_{\text{c} = 1}^\text{last cell}
    \rho [\text{c},t]
    \texttt{t}_i[\text{c},t]dv[c],
    \\ 
    \textbf{x}_i(t)
    = 
    \frac{1}{m_i(t)}
    \sum_{\text{c} = 1}^\text{last cell}
    \textbf{x} 
    \rho [\text{c},t]
    \texttt{t}_i[\text{c},t]dv[c],
    \\ 
    \textbf{u}_i(t)
    = 
    \frac{1}{m_i(t)}
    \sum_{\text{c} = 1}^\text{last cell}
    \textbf{u} [\text{c},t]
    \rho [\text{c},t]
    \texttt{t}_i[\text{c},t]dv[c],
\end{align*}
where the sum from ``$\text{c} = 1$'' to ``$\text{last cell}$'' denotes a summation over the entire mesh grid, and $\rho[\text{c},t]$ and $\textbf{u}[\text{c},t]$ are the density field and velocity field evaluated at the cell ``c'' and at a simulation time step $t$. 
Likewise, $\textbf{x}[\text{c}]$ and $dv[c]$ correspond to the Cartesian coordinate and the volume of the cell, respectively. 

For a given time step $t_n$, we compute the position $\textbf{x}_i(t_n)$ and velocity $\textbf{u}_i(t_n)$ of each droplet. 
Then, by measuring each particle pair distance, we identify the nearest neighbor for each droplet $i$. 
For convenience the nearest neighbor of the droplet $i$ is indexed $j$. 
Once this is done we are able to compute the relative positions $\textbf{r}_{ij}(n) =\textbf{x}_i - \textbf{x}_j$, and the relative velocities $\textbf{w}_{ij} = \textbf{u}_i - \textbf{u}_j$ with the nearest neighbor for all droplets. 
At the simulation time step $t_{n+1}$ we repeat this procedure and compute all the $\textbf{x}_i(t_{n+1}),\;\textbf{u}_i(t_{n+1}),\;\textbf{r}_{ij}(t_{n+1}),\;\textbf{w}_{ij}(t_{n+1})$. 
If the nearest neighbor of the droplet $i$ at $t = t_{n+1}$, is still the same as at $t = t_n$, we increment the \textit{age} of interaction as $a_i = a_i + (t_{n+1} - t_n)$, where $a_i$ is the \textit{age} of the particle $i$. 
Inversely, if the particle $j$ of time $t= t_{n+1}$ is not the same as the one of time $t=t_n$ the \textit{age} is set back to zero. 
Note that at $t = 0$ all ages are set top zero. 


To reconstruct all these statistics from the DNS, we treat each simulation time step and droplets as an independent event, denoted as, $\FF$. 
As an example, to reconstruct a quantity such as $\textbf{w}^\text{nst}_p(\textbf{x},\textbf{r},t,a)$ we gather the relative velocities $\textbf{w}_{ij}(t)$ from the simulation and store them in $i$ intervals of ages $\Delta a_k$, and relative positions $\Delta \textbf{r}_k$ for $k = 1,\ldots, n$.
Then, we average on all the $\textbf{w}_{ij}(t;\FF)$ over each particle and time step.
Formally, we write, 
\begin{equation}
    \textbf{w}^\text{nst}_p(\Delta\textbf{r}_k,\Delta a_k)
    = \frac{1}{E_k} 
    \sum^{E_k}_{\FF_k} 
    % \sum_i^{N_b}
    % \sum_{j\neq i}^{N_b}
    \textbf{w}_{ij}(t;\FF_k)
    % h_{ij}
    % \text{\;\;  with  \;\;}
    % \FF_k = \{\FF; \textbf{r}(\FF)\in\Delta \textbf{r}_k, a(\FF)\in  \Delta a_k\}
    \label{eq:vec_cond}
\end{equation}
where $\FF_k$ correspond to the events were the nearest particle pair $i$ and $j$ follows $\textbf{r},a \in \Delta \textbf{r}_k ,\Delta a_k$.
$E_k$ is the total number of events fulfilling these constraints. 
% Thus, we obtained an approximation of $\textbf{w}^\text{nst}_p(\textbf{x},\textbf{r},t,a)$ which takes the intervals, $(\Delta\textbf{r}_i,\Delta a_i)$ as arguments.
At some point, it will be useful to study the averaged relative velocity, conditioned on the age or on the radial distance, independently. 
Therefore, in a more general way if $p$ is a scalar property with $\Delta p_k$ its $n$ intervals, we can define the $p$-conditionally averaged relative velocity as, 
\begin{equation}
    \textbf{w}^\text{nst}_p(\Delta p_k)
    = \frac{1}{E_{k}} 
    \sum^{E_{k}}_{\FF_{k}}  
    % \sum_i^{N_b} 
    % \sum_{j\neq i}^{N_b}
    \textbf{w}_{ij}(t;\FF_k)
    % h_{ij}
    % \text{\;\;  with  \;\;}
    % \FF_k = \{\FF; p(\FF)\in\Delta p_k\}
    \label{eq:scalar_cond}
\end{equation}
In this definition, $\FF_{k}$ corresponds to all the events where the nearest neighbors respect the condition, $p \in \Delta p_k$, and $E_{k}$ represents the total number of events fulfilling this constraint. 

Note that due to the average over the macroscopic variables, $\textbf{w}_p^{nst}(\Delta\textbf{r}_k,\Delta a_k)$ and $\textbf{w}^\text{nst}_p(\Delta p_k)$ is dependents on $\textbf{x}$ and $t$. 
In general this will be the case for all quantity presented in \ref{sec:results}. 
Therefore, from now on we drop the \textbf{x} and $t$ arguments. 


It is clear that to obtain representative averaged quantities, the number of events $E_k$ per intervals must be consequent. 
For 2D-conditioned quantity such as \ref{eq:vec_cond}, we estimated that $100$ samples per bins were sufficient to obtain good qualitative results. 
Consequently, the plots exposed in \ref{sec:results} have been generated by averaging the quantity of interest (velocity fields, age of interaction) with a minimum threshold of $E_k = 100$ samples for each bin.
Regarding the scalar-conditioned fields such as in \ref{eq:scalar_cond}, we gathered $E_k = 1000$ sample per bins to obtain accurate and quantitative results. 
Lastly, regarding the sampling, we collected data for each Lagrangian quantity every $10$ simulation time steps.
On average, $200,000$ time steps are performed during a simulation with $N_b = 125$ droplets. 
This results in a total number of $E = 2,500,000$ samples. 
In \ref{ap:validation}, we demonstrate that our statistics are well-converged.

