
\section{Ellipsoidal surface tension stress}
\label{ap:surface_tension}
\tb{METTRE A JOUR LES FORMULES}
In this section we provide the detailed calculation of te surface tension stress tensor for ellipsoidal particles. 

In indices notation,  
\begin{equation*}
    \sigma_{I,ij}^0 =\gamma\left[
    \delta_{ij} - \frac{ H_{ik} H_{jl} :  r_kr_l}{  H_{ab}  H_{ac} r_br_c} \right]
\end{equation*}
Integrating this over a surface will eventually leads to an elliptic integral due to the elliptical surface. 

If the spheroid is aligned with the principal axes $\textbf{H} = \textbf{e}_1\textbf{e}_1 / a^2(t) + (\textbf{e}_2\textbf{e}_2+ \textbf{e}_3\textbf{e}_3)/b^2(t)$.
Thus, $\textbf{H}\cdot \textbf{r} = H_{ij} r_j = {e}_{1,i}{e}_{1,j}r_j / a^2(t) + ({e}_{2,i}{e}_{2,j} + {e}_{3,i}{e}_{3,j})r_j/b^2(t) $ which gives, the vector, 
$\textbf{H}\cdot \textbf{r} = \textbf{e}_{1} x/ a^2(t) + (\textbf{e}_{2}y + \textbf{e}_{3}z)/b^2(t)  = \textbf{e}_i r_i /a_i^2$
Consequently, the second term of the last equality reads in a main axis as, 
\begin{equation*}
    \frac{ H_{ik} H_{jl} :  r_kr_l}{  H_{ab}  H_{ac} r_br_c} 
    = \textbf{e}_i \textbf{e}_j \frac{ r_i r_j /(a_i a_j)^2 }
    {\frac{z^2}{a^4}+\frac{y^2+x^2}{b^4}}
\end{equation*}
To dealt with this ellipsoid integral we may employ the following change of variable :
\begin{align*}
    x = b \sin \theta \cos \phi\\
    y = b \sin \theta \sin \phi\\
    z = a \cos \theta 
\end{align*}
with $\theta \in [0,\pi]$ and $\phi \in [0,2\pi]$. 
The point on the ellipsoid surface can then be written as $\textbf{v} = [x(\theta,\phi),y(\theta,\phi),z(\theta,\phi)]$. 
Now let's first consider the surface calculation, in our coordinate system we have, 
\begin{equation*}
    \iint_S dS
    = 
    \int_{0}^{2\pi}
    \int_{0}^{\pi}
    \left|\frac{\partial \textbf{v}}{\partial \theta} 
    \times 
    \frac{\partial \textbf{v}}{\partial \phi} \right|
    d\theta
    d\phi
\end{equation*}
The partial derivative reads, 
\begin{align*}
    \frac{\partial \textbf{v}}{\partial \theta}
    = 
    b \cos \theta \cos \phi \textbf{e}_x
    + b \cos \theta \sin \phi\textbf{e}_y
    - a \sin \theta \textbf{e}_z
    \\
    \frac{\partial \textbf{v}}{\partial \phi}
    = 
    - b \sin \theta \sin \phi \textbf{e}_x
    + b \sin \theta \cos \phi\textbf{e}_y
\end{align*}
Taking the norm of the above vector cross product yields the relation : 
$dS = \left|\frac{\partial \textbf{v}}{\partial \theta} 
\times 
\frac{\partial \textbf{v}}{\partial \phi} \right| d\theta d\phi = b \sin\theta (a^2\sin^2\theta+ b^2 \cos^2\theta)^{1/2}d\theta d\phi$. 

Injecting these coordinate into the previous integrand formula for the dyadic normal reads, 
\begin{equation*}
    \frac{ H_{ik} H_{jl} :  r_kr_l}{  H_{ab}  H_{ac} r_br_c} 
    = \textbf{e}_i \textbf{e}_j \frac{ r_i r_j /(a_i a_j)^2 }
    {\frac{1}{a^2}\cos^2 \theta+\frac{1}{b^2}\sin^2 \theta (\cos^2 \phi+ \sin^2 \phi)}
    = \textbf{e}_i \textbf{e}_j \frac{ r_i r_j}
    {\frac{(a_i a_j)^2}{a^2}\cos^2 \theta+\frac{(a_i a_j)^2}{b^2}\sin^2 \theta }
\end{equation*}
Due to symmetry consideration the crossed terms are all null thus the remaining terms to evaluate are just the diagonal terms. 
The first term of the surface stress, that we call $S_1$ is the surface energy, i.e. the surface of the ellipsoid times the surface tension coefficient $\gamma$. 
\begin{equation*}
    (S_1)_{ij} 
    = \delta_{ij} 2\pi 
    \int_0^\pi 
    b \sin\theta (a^2\sin^2\theta+ b^2 \cos^2\theta)^{1/2} d\theta 
    = 2\pi b \left[\frac{a^2}{\sqrt{b^2-a^2}} \text{asinh}\left(\frac{\sqrt{b^2-a^2}}{a}\right)+b\right]
\end{equation*} 
where $\text{asinh}$ is the Hyperbolic Arc Sine function.
Note that the surface can be reformulated as,  
\begin{equation*}
    s_\alpha
    = 2\pi b \left[\frac{a^2}{\sqrt{b^2-a^2}} \text{ln}\left(\frac{b + \sqrt{b^2-a^2}}{a}\right)+b\right]
\end{equation*} 
which is more convenient. 
This expression is consistent with the classic ex pression of an ellipsoid surface. 
Now let's compute the integral $S_{2,zz}$ it reads, 
\begin{align*}
    S_{||}
    = 
    \gamma\int_0^{2\pi}\int_0^{\pi}\left[
        \frac{\cos^2\theta}{\cos^2 \theta+\frac{a^2}{b^2}\sin^2 \theta }
    \right]
    b \sin\theta (a^2\sin^2\theta+ b^2 \cos^2\theta)^{1/2} d\theta d\phi\\
    = 
    \gamma\int_0^{2\pi}\int_0^{\pi}\left[
        \frac{\cos^2\theta}{b^2\cos^2 \theta+a^2\sin^2 \theta }
    \right]
    b^3 \sin\theta (a^2\sin^2\theta+  b^2\cos^2\theta)^{1/2} d\theta d\phi\\
    = 
    \gamma 2\pi \int_0^{\pi}
    b^3 \cos^2\theta\sin\theta (a^2\sin^2+  b^2\cos^2\theta)^{-1/2} d\theta\\
    = \gamma 2\pi  b^3\,\left({{2\,b}\over{2\,b^2-2\,a^2}}-{{a^2\,{\rm asinh}\; \left(
    {{\sqrt{b^2-a^2}}\over{a}}\right)}\over{\left(b^2-a^2\right)^{{{3
    }\over{2}}}}}\right)
\end{align*}
Now let's see for the perpendicular components, namely, 
\begin{align*}
    S_{\bot}
    = 
    b a^2\gamma\int_0^{2\pi}\sin^2\phi d\phi 
    \int_0^{\pi}
        \sin^2\theta
    \sin\theta (a^2\sin^2\theta+ b^2 \cos^2\theta)^{-1/2} d\theta \\
    = 
    b a^2\gamma \pi
    \int_0^{\pi}
    \sin^3\theta (a^2\sin^2\theta+ b^2 \cos^2\theta)^{-1/2} d\theta \\
\end{align*}

The final results is the following, 
The surface tension stress can be written in terms of the two principal axis of the ellipsoid in the laboratory reference frame with, 
\begin{equation*}
    \intS{\bm{\sigma}_I^0}
    = \frac{2}{3} s_\alpha \gamma \textbf{I} + \textbf{pp} (-2 S)  + (\textbf{I} - \textbf{pp}){S}
\end{equation*}
where the first term is the isotropic part consisting into the surface energy and the second and third terms correspond to the components of anisotropy of the surface stress, namely, 
\begin{align*}
    S
    = 
    {{\left(\pi\,a^4\,b-4\,\pi\,a^2\,b^3\right)\,\log \left({{\sqrt{b^2
    -a^2}+b}\over{a}}\right)+\sqrt{b^2-a^2}\,\left(2\,\pi\,b^4+\pi\,a^2
    \,b^2\right)}\over{\sqrt{b^2-a^2}\,\left(3\,b^2-3\,a^2\right)}}
\end{align*}
We recall that this quantity drives the stress jump at the interface. 
As it is expected this stress jump is axis symmetric around the particle main axis. 
Besides, it is maximum at the poles and minimum at the equator of the particle. 
It is then possible to compute the integral of the stress by direct integration in the reference frame of the ellipsoid principal axes. 
The exact result yields, 
\begin{equation*}
    \gamma\pSavg{\textbf{I}-\textbf{nn}}
    = \gamma \left[
        \frac{2}{3} s_\alpha \textbf{I}
        + S (\textbf{I}-\textbf{pp}) -2S\textbf{pp}
        \right]
\end{equation*}
where the first component correspond to the isotropic part of the surface stress, and the second component to the deviatoric part of the surface stress. 
Notice that the deviatoric part of this tensor is function of one unique coefficient, $S$ due to the axis symmetrical nature of the droplets. 
Exact solution can be given in terms of the small deformation parameter $e_\bot = b/r$. 
Then an approximation can be deduced for the $e -1 \ll 1$, it gives,
\begin{align*}
    s_\alpha 
    = 4\pi r^2 \left[\frac{e_\bot^2}{2} + \frac{\ln\left(\sqrt{{e_\bot^6}-1}+{e_\bot^3}\right)}{2e_\bot\sqrt{e_\bot^6-1}}\right]
    = 4 \pi r^2 + \frac{24 v }{5 r} (e_\bot-1)^2\\
    S = \frac{4}{3} \pi r^2 \left[
    \frac{\left( \frac{1}{4} - e_\bot^6\right)  \log{\left( \sqrt{e_\bot^6-1}+{e_\bot^3}\right) } }
    { e_\bot  \left( e_\bot^6- 1\right)^{3/2} }
    +  \frac{e_\bot^2\left( e_\bot^6+  \frac{1}{2}\right)}{2\left( e_\bot^6- 1\right)}  \right]
    \approx 
    \frac{8 v}{5 r}(e_\bot-1) + \frac{12 v }{35r}(e_\bot-1)^2 \ldots
\end{align*}
\tb{METTRE A JOUR LES FORMULES}
Regarding the expression of the surface of the spheroid, it can be noticed that the function within bracket tends to $1$ for $e=1$ leaving us with $s_\alpha = 4\pi r^2$ which is the surface of the sphere. 
Then, it slowly increases when $e$ is either superior or inferior to $1$. 

Equally, the results can be expressed in terms of the deformation parameter $e_{||} = a/r$ in which case the previous results give at the second order in $e_\bot-1$ the following expression, 
\begin{align*}
    s_\alpha 
    \approx 4 \pi r^2 + \frac{6 v }{5 r} (e_{||}-1)^2 \ldots\\
    S 
    \approx 
    - \frac{4 v}{5 r}(e_{||}-1) + \frac{24 v }{35r}(e_{||}-1)^2 \ldots
\end{align*}
Noticing that the strain tensor $\textbf{C} = (e_{||}-1) \textbf{pp} + (e_\bot-1)(\textbf{I}- \textbf{pp})$ one can finally write,
\begin{align*}
    \gamma\pSavg{\textbf{I}-\textbf{nn}}
    = \frac{\gamma v}{r} \left[
        2  + \frac{1 }{15 } (\textbf{C}:\textbf{C})\right] \textbf{I}\\
        + \frac{\gamma v}{r} \left[ \frac{8}{5} \textbf{C}
        + \frac{12}{35}[\textbf{C}\cdot \textbf{C}- 6 (\textbf{C}:\textbf{pp})^2\textbf{pp}]
        \right]
\end{align*}
This gives the surface stress tensor up to the second order terms in accuracy. 
To our knowledge this has never been proposed. 
\tb{check in better details}

\section{A translating spherical droplet in stokes}
\label{ap:Translating_sphere}
In this appendix we expose the velocity fields solution for the stokes flow past a spherical drop. 
In a second step, we compute the form of the moment of momentum closure mentioned in \ref{sec:Lagrangian} in terms of the fluid properties and the drop fluid relative velocity.

We consider a drop of radius $a$ translating with the velocity $\textbf{u}_\alpha$ in a stokes flow with undisturbed velocity $\textbf{u}_1$.
The relative velocity between the droplet and the fluid is defined as $\textbf{u}_{\alpha 1}= \textbf{u}_\alpha - \textbf{u}_1(\textbf{x}_\alpha)$ where $\textbf{u}_1(\textbf{x}_\alpha)$ is the undisturbed averaged fluid velocity at the position $\textbf{x}_\alpha$. 
In these conditions, the local fluid phase velocity $\textbf{u}_1^0$, the local particle interior velocity $\textbf{u}_2^1$ and the local stress fields $\bm\sigma_2^0$ within the particle phase, might be written as\citet{pozrikidis1992boundary}\footnote{The solution of this problem is derived in the above cited book p .207.  However, the author made a slight mistakes on the constant $\textbf{c}$ which we corrected here. }, 
\begin{align*}
    u_{1,i}^0
    = \left(\frac{\delta_{ik}}{r} + \frac{r_ir_k}{r^3}\right)  g_k
    + \left(-\frac{\delta_{ik}}{r^3} + \frac{3r_ir_k}{r^5}\right)  d_k\\
    u_{2,i}^0
    = c_i
    + \left(2 r^2 \delta_{ik} - r_ir_k\right) e_k\\
    % e_{2,ik}^0
    % = \mu(
    %     3 \delta_{ij} r_k 
    %     + 3 \delta_{kj} r_i
    %     -2 r_j \delta_{ki}
    % )e_j 
    \sigma_{2,ik}^0
    = \mu 3(
        - 4 \delta_{ik} r_j
        + \delta_{ij} r_k
        + r_i \delta_{kj}
    )e_j 
\end{align*}
with, 
\begin{align*}
    &\textbf{g} = a\frac{1}{4}\left(\frac{3\lambda + 2}{\lambda +1}\right) \textbf{u}_{\alpha 1},
    &\textbf{d} = -a^3\frac{1}{4}\left(\frac{\lambda}{\lambda +1}\right) \textbf{u}_{\alpha 1},\\
    &\textbf{c} = \frac{1}{2}\left(\frac{2\lambda + 3}{\lambda +1}\right) \textbf{u}_{\alpha 1},
    &\textbf{e} = -\frac{1}{a^2}\frac{1}{2}\left(\frac{1}{\lambda +1}\right)  \textbf{u}_{\alpha 1}.\\
\end{align*}

Now that we have an explicit solution for the internal flow and stress one can compute the terms appearing in the energy and moment of momentum balance equations. 
The integral involving the particle internal motion in the equation exposed in \ref{sec:Lagrangian} are evaluated exhaustively and yield, 
\begin{equation*}
    \intO{\rho_2(\textbf{w}_2^0)_i (\textbf{w}_2^0)_j}
    = \frac{m_\alpha}{140 (\lambda +1)^2}
    (7 (\textbf{u}_{\alpha 1})_i(\textbf{u}_{\alpha 1})_j + (\textbf{u}_{\alpha 1}\cdot \textbf{u}_{\alpha 1})\delta_{ij})
\end{equation*} 
\begin{equation*}
    \intO{\rho_2(\textbf{w}_2^0)_k (\textbf{w}_2^0)_k}
    = \frac{m_\alpha}{14 (\lambda +1)^2}
     (\textbf{u}_{\alpha 1})_k(\textbf{u}_{\alpha 1})_k
\end{equation*} 
\begin{equation*}
    \intO{\rho_2(\textbf{w}_2^0)_i (\textbf{w}_2^0)_j}^\text{dev}
    = \frac{m_\alpha}{20 (\lambda +1)^2}
    ((\textbf{u}_{\alpha 1})_i(\textbf{u}_{\alpha 1})_j + (\textbf{u}_{\alpha 1}\cdot \textbf{u}_{\alpha 1})\delta_{ij})
\end{equation*} 
\begin{equation*}
    \intO{\bm\sigma_2^0}
    = 0 
\end{equation*}
\begin{equation*}
    \intO{\bm{\sigma}_2^0:\grad \textbf{u}_2^0}
    = 2\mu_2 \intO{\textbf{e}_2^0: \textbf{e}_2^0 }
    = 
    \frac{6 \mu_2 v_p}{a^2(1+\lambda)^2}
    (\textbf{u}_{\alpha 1}\cdot \textbf{u}_{\alpha 1})
\end{equation*}
\begin{align*}
    \intO{\textbf{r}\textbf{u}_2^0}
    = 0 
\end{align*}
\begin{equation*}
    \intS{\bm\sigma_1^0\cdot \textbf{n}_2}
    = - \frac{3v_\alpha\mu_1}{2 a^2} 
    \left(\frac{3\lambda+2}{\lambda+1}\right) 
    \textbf{u}_{\alpha 1}
\end{equation*}
\begin{equation*}
    \intS{\textbf{r}\bm\sigma_2^0\cdot \textbf{n}_2}
    = 0 
\end{equation*}
\begin{equation*}
    \intS{(\bm\sigma_2^0\cdot \textbf{n}_2)_i r_kr_l}
    = \frac{3\mu_1\phi_2}{10}\left(\frac{5\lambda+2}{\lambda+1}\right)u_{1 \alpha,i}\delta_{kl}
    + \frac{3\mu_1\phi_2}{5}\left(\frac{1}{\lambda+1}\right)(u_{1 \alpha,k}\delta_{il}+u_{1 \alpha,l}\delta_{ki})
\end{equation*}
\begin{equation*}
    \intO{\mu(\textbf{e}_2^0)_{ik} r_l} =
    \frac{\phi_2\mu_1}{10}\left(\frac{1}{\lambda+1}\right)
    \left(
        2\delta_{ik}u_{1 \alpha , l}
        -3\delta_{kl}u_{1 \alpha , i}
        -3\delta_{il}u_{1 \alpha , k}
    \right)
\end{equation*}
We can notice that now all these quantities are determined by the relative velocity.  
While the hill vortex is a solution valid in potential and stokes flow, the solution for the exterior flow is limited to stoke flow. 
Consequently, the zero, first and second moment of surface force are limited to stokes flow. 

\section{A translating oblate spheroidal droplet in stokes}

In this appendix we expose the velocity fields solution for the stokes flow past a spherical drop. 
In a second step, we compute the form of the moment of momentum closure mentioned in \ref{sec:Lagrangian} in terms of the fluid properties and the drop fluid relative velocity.

We consider a drop of radius $a$ translating with the velocity $\textbf{u}_\alpha$ in a stokes flow with undisturbed velocity $\textbf{u}_1$.
The relative velocity between the droplet and the fluid is defined as $\textbf{u}_{\alpha 1}= \textbf{u}_\alpha - \textbf{u}_1(\textbf{x}_\alpha)$ where $\textbf{u}_1(\textbf{x}_\alpha)$ is the undisturbed averaged fluid velocity at the position $\textbf{x}_\alpha$. 
In these conditions, the local fluid phase velocity $\textbf{u}_1^0$, the local particle interior velocity $\textbf{u}_2^1$ and the local stress fields $\bm\sigma_2^0$ within the particle phase, might be written as linear combinaison of spherical harmonique proportional to $\textbf{u}_{1\alpha} = U$ thus
\begin{align*}
    u_{1,i}^0
    = \left(\frac{\delta_{ik}}{r} + \frac{r_ir_k}{r^3}\right)  g U_k
    + \left(-\frac{\delta_{ik}}{r^3} + \frac{3r_ir_k}{r^5}\right)  d U_k\\
    p_1^0 = 
    \mu g U_j 2\frac{r_j}{r^3}\\
    u_{2,i}^0
    = c U_i
    + \left(2 r^2 \delta_{ik} - r_ir_k\right) e U_k\\
    p_2^0 
    = 10\mu e U_j r_j
\end{align*}
The stress is express as, 
\begin{align*}
    \sigma_{2,ij}^0 
    = - p_2^0 \delta_{ij}
    +\mu_2 (\partial_i u_{2,j}^0 + \partial_j u_{2,i}^0)
\end{align*}

\section{A droplet in shear flow}

We consider an infinite linear flow $\textbf{u}^\infty = \bm\Gamma\cdot \textbf{r} =(\bm\Omega + \textbf{E})\cdot \textbf{r} $ such that the undisturbed flow around the sphere is $\textbf{u}^\infty = \bm\Gamma\cdot\textbf{r}$.
The disturbance flow in this case might be determined following the method outlined in \citep{leal2007advanced}, we obtain  :
\begin{align*}
    \textbf{u}^0_1
    = \bm\Gamma\cdot\textbf{r}
    -\frac{\lambda}{(\lambda + 1)r^5} \textbf{E}\cdot\textbf{r}
    - \left(\frac{5\lambda +2}{2(\lambda +1 )r^5} - \frac{5\lambda}{2(\lambda+1)r^7}\right) \textbf{r}(\textbf{E}:\textbf{rr})\\
    p_1^0 
    = -\frac{(5\lambda+2)}{(\lambda+1)r^5}\textbf{E}:\textbf{rr}\\
% \end{align*}
% \begin{align*}
    \textbf{u}^0_2
    = \bm\Omega\cdot\textbf{r}
    + \frac{5r^2- 3}{2(\lambda + 1)} 
    \textbf{E}\cdot\textbf{r}
    -\frac{1}{\lambda+1} \textbf{r}(\textbf{E}:\textbf{rr})\\
    p_2^0 
    = \frac{21\lambda}{2(\lambda+1)}
    \textbf{E}:\textbf{rr}
\end{align*}

With that we are able to compute the following integrals,
\begin{equation*}
    \intO{\rho_2(\textbf{w}_2^0)_i (\textbf{w}_2^0)_j}
    = \frac{4\pi}{15}\bm\Omega\cdot\bm\Omega
    + \frac{4\pi}{945(\lambda+1)^2}
    (2\textbf{E}:\textbf{EI} + 15 \textbf{E}\cdot \textbf{E})
\end{equation*}
\begin{equation*}
    \intO{\rho_2(\textbf{w}_2^0)_k (\textbf{w}_2^0)_k}
    = \frac{4\pi}{15}\bm\Omega:\bm\Omega
    + \frac{4\pi}{45(\lambda+1)^2}
    \textbf{E}:\textbf{E} 
\end{equation*} 
\begin{equation*}
    \intO{\bm\sigma_2^0}
    = \frac{8\pi}{5(\lambda+1)}
    \textbf{E}
\end{equation*}
\begin{equation*}
    \intO{\textbf{e}_2^0}
    = \frac{8\pi}{3(\lambda+1)}
    \textbf{E}
\end{equation*}
\begin{equation*}
    \intO{\bm{\sigma}_2^0:\grad \textbf{u}_2^0}
    = 2\mu_2 \intO{\textbf{e}_2^0: \textbf{e}_2^0 }
    = 
    \frac{4\pi}{(\lambda+1)^2}\textbf{E}:\textbf{E}
\end{equation*}
\begin{align*}
    \intO{\textbf{r}\textbf{u}_2^0}
    = 0 
\end{align*}
\begin{equation*}
    \intS{\bm\sigma_1^0\cdot \textbf{n}_2}
    = 0
\end{equation*}
\begin{equation*}
    \intS{\textbf{r}\bm\sigma_1^0\cdot \textbf{n}_2}
    = \frac{4\pi}{5}\frac{5\lambda+2}{\lambda+1}\textbf{E} 
\end{equation*}
\begin{equation*}
    \intS{(\bm\sigma_2^0\cdot \textbf{n}_2)_i r_kr_l}
    = 0
\end{equation*}
\begin{equation*}
    \intO{\mu(\textbf{e}_2^0)_{ik} r_l} =
    0
\end{equation*}