\section*{fluid phase stress}
Already, we can see that the equivalent stress of the fluid phase is the made of the average fluid stress represented by the two first terms on the right hands side of \ref{eq:sigma_eq_0}. 
The first moment $\pSavg{\textbf{r}\bm{\sigma}_1^0 \cdot \textbf{n}_2}$ appearing in \ref{eq:sigma_eq_0} posses a skew-symmetric part and a symmetric part, the latter corresponding to the stresslet (see \ref{eq:stresslet_def}).
However, for non-solid particles \ref{eq:stresslet_def} is not entirely valid since in stokes theory the quantity referred as the stresslet is defined as \citet{pozrikidis1992boundary,kim2013microhydrodynamics},
\begin{equation}
    \label{eq:stresslet_def}
    n_p \mathscr{S}_{p,ki}
    = \frac{1}{2}
    \pSavg{
        r_k \sigma_{il}n_l + r_i \sigma_{kl}n_l 
        - \delta_{ik}
        \frac{2}{3}
        r_l \sigma_{lk}n_k
        - 2 \mu_f (u_k n_i+u_i n_i)
    }
\end{equation}
Likewise, we introduce the average skew symmetric part $\mathscr{L}_p$ and the average trace of the first moments $\mathscr{D}_p$ such as, 
\begin{align}
    \label{eq:torque_def}
    n_p \mathscr{L}_{p,ki}
    = \frac{1}{2}\pSavg{ r_k \sigma_{il}n_l - r_i \sigma_{kl}n_l }\\
    \label{eq:trace_def}
    n_p \mathscr{D}_{p,ij}
    = \frac{1}{3}\pSavg{ r_k (\sigma_{kl} + p_1 \delta_{kl})n_l } \delta_{ij}
    - n_p v_p p_1 \delta_{ij}
\end{align}
where we have retrieved the mean pressure from the trace of the first moments, so that we make appear the hydrostatic pressure  $n_p v_p p_1 \bm\delta$ explicitely.  
Notice that the volume fraction $\phi_1$ is present in front of the averaged pressure terms in \ref{eq:sigma_eq_0}.  
In various study \citep{prosperetti2009computational,chu2016flux}, this term is shown to be problematic  since it might generate nonphysical flux of momentum. 
However, as shown above and pointed out by  \citet{zhang1997momentum,jackson1997locally}, the first moment of hydrodynamic force tensor contains a part of the hydrostatic pressure.
With that contribution the total pressure in the fluid stress reach $\phi_1p_1 + n_p p_1 \approx p_1$ which is consistent.
Additionally, as seen in \ref{sec:two-fluid} the Reynolds stress is related to the pseudo turbulent kinetic energy through $\avg{\chi_1 \rho_1\textbf{u}_1'\textbf{u}_1'} : \bm\delta = 2k_1$ . 
Therefore, we can write, $\avg{\chi_1 \rho_1\textbf{u}_1'\textbf{u}_1'} = 2 \rho_1 k_1 \bm\delta + \avg{\textbf{u}_1'\textbf{u}_1'}^\text{dev}$ where the second term is the deviatoric part of the Reynolds stress. 

These remarks motivate us to rewrite the equivalent fluid phase stress under the general expression,  
\begin{multline*}
    \bm{\sigma}_1^\text{eq}
    = 
    \underbrace{p_1  \bm\delta
    - \mu_1 \textbf{e} }_\text{Newtonian fluid stress}
    +  \underbrace{\phi_1 k_1 \bm\delta
    + \rho_1 \avg{\chi_1\textbf{u}_1'\textbf{u}_1'}^\text{dev}}_\text{fluctuating stresses}
    - \underbrace{(n_p \mathscr{S}_p
    + n_p \mathscr{L}_p
    + n_p \mathscr{D}_p )}_\text{interfacial particles stresses}\\
    % + \mu_1  \pSavg{{\textbf{u}_1\textbf{n}_2 + \textbf{n}_2 \textbf{u}_1}}
    % - n_p \textbf{F}_\text{p}
    % + n_p \textbf{F}_\text{pfp} 
    + \frac{1}{2} \div \underbrace{\left[
        \pSavg{\textbf{rr}\bm{\sigma}_1^0\cdot \textbf{n}_2}
        + 2\pOavg{\mu_1 \textbf{re}_2^0 }
        + \ldots
        \right]
        }_\text{inhomogeneous particles stresses}
    \label{eq:sigma_eq1_def}
\end{multline*}
% with, 
% \begin{equation*}
%      \bm{\Sigma}
%     = 
%      \pMSavg{\textbf{rr} \bm{\sigma}_1^0\cdot \textbf{n}_2}
%      -\pMOavg{\mu_1 \textbf{r} \textbf{e}_2 }\\
% \end{equation*}
The contribution of the fluid phase equivalent pressure is made of,
the averaged $p_1$, the fluctuating part of the moment of force traction $\mathscr{D}_p$, and the fluid pseudo turbulent energy, $\phi_1 k_1$. 
The deviatoric part of the stress is constituted of the deviatoric part of the Reynolds stress $\avg{\chi_1\textbf{u}_1'\textbf{u}_1'}^\text{dev}$, the mean fluid shear rate $\mu_1 \textbf{e}$, the stresslet $\mathscr{S}_p$ and the hydrodynamic torque $\mathscr{L}_p$. 
The higher order moments found in $\bm{\Sigma}$ are not necessarily negligible, as shown in \citet{lhuillier1996contribution,jackson1997locally}, in fact they exhibit a different physical meaning. 
The first order moments will be function of the mean gradient of the fluid velocity while the other will be function of the background relative motion. 

\tb{a enlever}
It is known that the $n_p \mathscr{S}_p$ plays a significant role in the determination of the equivalent viscosity of the mixture. 
Therefore, it is of major importance to be able to measure it in DNS or experiment.
As, demonstrated by the expression of the ensemble averaged stress it is quite difficult to obtain such an information by experimental means, since it is mixed among other stresses.  
In DNS however we have access to pretty much any information, nevertheless surface integration of the stress can be shown to be inaccurate when performing volume of fluid method. 
Therefore, we propose the following formulas based on \ref{eq:dt_hybrid_Sp} which enable us to compute the stresslet by almost only volume integration,  


The last integral accounting for surface tension cannot be converted to volume integral. 
However, this integral is related only to the geometry of the interface. 
Besides, note that the pressure is absent as $\mathscr{S}_p$ is traceless. 

\begin{multline}    
    + n_p \mathscr{S}_p
    =
    \frac{1}{2}\pavg{\ddt^2{\textbf{M}_\alpha^\text{dev}}}
    - \pOavg{\left(
    \rho_2\textbf{w}_2^0 \textbf{w}_2^0
    - \rho_2\frac{1}{3}(\textbf{w}_2^0 \cdot \textbf{w}_2^0)\bm\delta\right)}\\
    + \mu_1 (\lambda - 1)\pOavg{\textbf{e}_2^0}
    + \pSavg{\gamma\left(\frac{1}{3}\bm\delta-\textbf{nn}\right)}\\
\end{multline}



\subsection{The bulk stress in dispersed multiphase flow}



Now that the architecture of the averaged dispersed multiphase flow equation is clarified, we would like to present the expression of the bulk stress tensor in a suspension of inertial particles subject to an arbitrary local body force field, $\textbf{b}^0$.
Firstly, is important to recall the definition of the \textit{bulk stress}. 
We define the \textit{bulk stress} tensor as a force applied on the fluid and on the particles phase, having the form $\div \bm{\Sigma}$, which added to the total external force $\textbf{B}$, balance exactly the material derivative of the mixture momentum : $\frac{D \rho \textbf{u}}{Dt}$. 
In this definition $\textbf{B}$ cannot be decomposed into a vector and a divergence of a tensor, in which case the latter would just contribute to $\bm{\Sigma}$.

We first expose the averaged mixture momentum and angular momentum equation easily derived from \ref{eq:dt_avg_f}, 
\begin{align}
    \pddt (\rho u_i)
    + \partial (\rho u_iu_k
    + \sigma_{ik}^\text{eq})
    = b_i\\
    \epsilon_{ijk} \sigma_{jk}
    = 0 
    \label{eq:momentum_bulk}
\end{align}
In the momentum equation we have defined, $\sigma_{ik}^\text{eq} = \avg{\rho\textbf{u}'\textbf{u}'}
- \avg{\chi_1\bm{\sigma}_1^0}-\avg{\chi_2\bm{\sigma}_2^0} - \avg{\delta_I \bm{\sigma}_I^0}$. 
Additionally, in the averaged angular momentum equation we have assumed that no-body torque exist at the local scale making the second equality equal to $0$ \citet{leal2007advanced} and the averaged mixture stress $\bm{\sigma}$ a symmetric quantity. 
However, note that $\bm{\sigma}$ is not exactly equal to the \textit{bulk stress} tensor $\bm{\Sigma}$ since $\textbf{b}$ can be expressed as a divergence of a stress.
Indeed, have defined $\textbf{b} = \textbf{B} + \div  \pMOavg{\textbf{b}_2^0}$ where $\textbf{B} = \phi_1 \textbf{b}_1 +  \pOavg{\textbf{b}_2^0 }$ and  $\pMOavg{\textbf{r}\textbf{b}_2^0}$ is defined accordingly to the previous definition. 
It follows the definition of the \textit{bulk stress} : 
\begin{equation}
    \bm{\Sigma}
    = 
    \avg{\rho\textbf{u}'\textbf{u}'}
    - \avg{\chi_1\bm{\sigma}_1^0}
    - \avg{\chi_2\bm{\sigma}_2^0} 
    - \avg{\delta_I \bm{\sigma}_I^0}
    - \pMOavg{\textbf{r}\textbf{b}_2^0}
\end{equation}
which proves already, in the absence of particles moments of the body forces $\pMOavg{\textbf{r}\textbf{b}_2^0}$, the antisymmetric part of the suspension stress is null, in agreement with \citet{dolata2020heterogeneous}.
% This skew symmetric part can be written in vector form as, 
% \begin{equation*}
%     \epsilon_{ijk}\textbf{T}_{jk}
%     = 
%     -\epsilon_{ijk} \pOavg{r_kb_j}
%     -\epsilon_{ijk}\frac{1}{2}\partial_l \pOavg{r_lr_kb_j}
%     = 0  
% \end{equation*}
We recall that the carrier fluid is a Newtonian fluid, therefore we may express the fluid phase stress as, 
\begin{equation}
    \phi_1 \sigma_{1,jk}
    = -p_1 \delta_{jk}
    + \mu_1 e_{jk}
    - \mu_1 \phi_2 e_{2,jk}. 
\end{equation} 
Additionally, we use the methodology of \citep{lhuillier1992volume,lhuillier1996contribution} to re express the averaged particle stress terms. 
The divergence of the particle phase stress may be expressed using \ref{eq:f_exp}, 
\begin{align}
    \label{eq:exp_sigma22}
    \partial_k \avg{\chi_2 {\sigma}_2^0}_{ik}
    &=  \partial_k\pOavg{ {\sigma}_{2,ik}^0}
    -\frac{1}{2} \partial_k\partial_j
    \pOavg{ r_j{\sigma}^0_{2,ik} + r_k\sigma^0_{2,ij}}
    + \ldots  \\
    \label{eq:exp_sigmaI2}
    \partial_k \avg{\delta_I {\sigma}^0_I}_{ik} 
    &=  \partial_k\pSavg{ {\sigma}_{I,ik}^0 }
        -\frac{1}{2} \partial_k\partial_j \pSavg{ r_j {\sigma}_{I,ik}^0+r_k {\sigma}_{I,ij}^0 }
        + \ldots  
\end{align}
Note that the heterogeneous terms must remain symmetric in the index $kj$ due to the double contraction with the operator $\partial_k\partial_j$, thus only the symmetric part in $jk$ remain and the terms such as, $\pOavg{ r_j{\sigma}^0_{2,ik} - r_k\sigma^0_{2,ij}}$ vanish. 
Upon the use of the moment of momentum equation of the first and second order we can easily derive these expressions, 
\begin{align}
    \intS{ (\bm{\sigma}_I)_{ik}}
    +\intO{ (\bm{\sigma}_2^0)_{ik}}
    = 
    \intO{ \rho_2 
    (\textbf{w}_2^0\textbf{w}_2^0  )_{ik}
    }
    -\ddt \intO{ r_i (\textbf{u}^0_2)_k }
    +\intS{ 
        b_{i}
        r_k 
    }
    +\intS{ 
     r_i (\bm{\sigma}_1^0 \cdot \textbf{n}_2)_{k}
    }
    \label{eq:dt_P_alpha}\\
    \intO{ r_{j}(\bm{\sigma}^0_2)_{ik}+r_{k}(\bm{\sigma}^0_2)_{ji}}
    +\intS{ r_{j}(\bm{\sigma}^0_I)_{ik}+r_{k}(\bm{\sigma}_I^0)_{ji}}
    = 
    - \ddt\intO{ \rho_2 (\textbf{u}_2^0)_i r_j r_k }\nonumber\\
    + \intO{ \rho_2 (r_{j} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_i + r_k (\textbf{w}_2^0)_j (\textbf{u}^0_2)_i)}
    +\intS{  r_{k}r_{j} (\bm{\sigma}_1^0)_{il} (\textbf{n}_2)_l }
    + \intO{ r_{k}r_{j}  \rho_2 b_i } 
    \label{eq:dt_P2_alpha}
\end{align}
It is evident that by using an arbitrary order of moment of momentum equation one can substitute any volume integral of the particle stress appearing in the expansion \ref{eq:exp_sigma22}. 
% By consideration of symmetric of the local stress, it is evident that the skew symmetric part of the moment of momentum will not have any dynamical role thus we can retrieve the average of \ref{eq:dt_mu_alpha} to the first relation. 
% To extract the skew symmetric part we start by writing the permutation of these equations with $ik$ yielding,  
% \begin{align}
%     \intS{ 
%     (\bm{\sigma}_I)_{ki}
%     }
%     +\intO{ 
%     (\bm{\sigma}_2^0)_{ki}
%     }
%     = 
%     \intO{ \rho_2 
%     (\textbf{w}_2^0\textbf{w}_2^0  )_{ki}
%     }
%     -\ddt \intO{ r_k (\textbf{u}^0_2)_i }
%     +\intS{ b_{k}r_i }
%     +\intS{ r_k (\bm{\sigma}_1^0 \cdot \textbf{n}_2)_{i}}\\
%     \intO{ r_{j}(\bm{\sigma}^0_2)_{ki}+r_{i}(\bm{\sigma}^0_2)_{jk}}
%     +\intS{ r_{j}(\bm{\sigma}^0_I)_{ki}+r_{i}(\bm{\sigma}_I^0)_{jk}}
%     = 
%     - \ddt\intO{ \rho_2 (\textbf{u}_2^0)_k r_j r_i }\nonumber\\
%     + \intO{ \rho_2 (r_{j} (\textbf{w}_2^0)_i (\textbf{u}^0_2)_k + r_i (\textbf{w}_2^0)_j (\textbf{u}^0_2)_k)}
%     +\intS{  r_{i}r_{j} (\bm{\sigma}_1^0)_{kl} (\textbf{n}_2)_l }
%     + \intO{ r_{i}r_{j}  \rho_2 b_k } \\
%     \intO{ r_{i}(\bm{\sigma}^0_2)_{jk}+r_{k}(\bm{\sigma}^0_2)_{ij}}
%     +\intS{ r_{i}(\bm{\sigma}^0_I)_{jk}+r_{k}(\bm{\sigma}_I^0)_{ij}}
%     = 
%     - \ddt\intO{ \rho_2 (\textbf{u}_2^0)_j r_i r_k }\nonumber\\
%     + \intO{ \rho_2 (r_{i} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_j 
%     + r_k (\textbf{w}_2^0)_i (\textbf{u}^0_2)_j)}
%     +\intS{  r_{k}r_{i} (\bm{\sigma}_1^0)_{jl} (\textbf{n}_2)_l }
%     + \intO{ r_{k}r_{i}  \rho_2 b_j } 
% \end{align}
% Acknowledgement of the symmetrical nature of $\bm{\sigma}_2^0$ and $\bm{\sigma}_I^0$ gives the following antisymmetrical balance equations, 
% \begin{align}
%     0
%     = 
%     -\ddt \intO{ r_i (\textbf{u}^0_2)_k -r_k (\textbf{u}^0_2)_i }
%     +\intS{ b_{i}r_k -b_{k}r_i }
%     +\intS{r_i (\bm{\sigma}_1^0 \cdot \textbf{n}_2)_{k} - r_k (\bm{\sigma}_1^0 \cdot \textbf{n}_2)_{i}}\\
%     \intO{ r_{j}(\bm{\sigma}^0_2)_{ik}
%             -r_{i}(\bm{\sigma}^0_2)_{jk}}
%     +\intS{ r_{j}(\bm{\sigma}^0_I)_{ik}
%            - r_{i}(\bm{\sigma}_I^0)_{jk}}
%     = 
%     - \ddt\intO{ \rho_2 (\textbf{u}_2^0)_i r_j r_k -  \rho_2 (\textbf{u}_2^0)_j r_i r_k }\nonumber\\
%     + \intO{ \rho_2 (r_{j} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_i + r_k (\textbf{w}_2^0)_j (\textbf{u}^0_2)_i)}
%     - \intO{ \rho_2 (r_{i} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_j + r_k (\textbf{w}_2^0)_i (\textbf{u}^0_2)_j)}\\
%     +\intS{  r_{k}r_{j} (\bm{\sigma}_1^0)_{il} (\textbf{n}_2)_l 
%     -r_{k}r_{i} (\bm{\sigma}_1^0)_{jl} (\textbf{n}_2)_l }
%     + \intO{ r_{k}r_{j}  \rho_2 b_i
%     - r_{k}r_{i}  \rho_2 b_j } 
% \end{align}
% The last equation need to be added to the second permutation which gives, 
% \begin{align*}
% \intO{ r_{j}(\bm{\sigma}^0_2)_{ik}}
% +\intS{ r_{j}(\bm{\sigma}^0_I)_{ik}}
% = 
% - \ddt\intO{ \rho_2 (\textbf{u}_2^0)_k r_j r_i 
% + \rho_2 (\textbf{u}_2^0)_i r_j r_k 
% -  \rho_2 (\textbf{u}_2^0)_j r_i r_k }\nonumber\\
% + \intO{ \rho_2 (r_{j} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_i + r_k (\textbf{w}_2^0)_j (\textbf{u}^0_2)_i)}
% - \intO{ \rho_2 (r_{i} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_j + r_k (\textbf{w}_2^0)_i (\textbf{u}^0_2)_j)}\\
% - \intO{ \rho_2 (r_{j} (\textbf{w}_2^0)_i (\textbf{u}^0_2)_k + r_i (\textbf{w}_2^0)_j (\textbf{u}^0_2)_k)}\\
% +\intS{  r_{k}r_{j} (\bm{\sigma}_1^0)_{il} (\textbf{n}_2)_l 
% +r_{j}r_{i} (\bm{\sigma}_1^0)_{kl} (\textbf{n}_2)_l 
% -r_{k}r_{i} (\bm{\sigma}_1^0)_{jl} (\textbf{n}_2)_l }
% + \intO{ r_{k}r_{j}  \rho_2 b_i
% + r_{j}r_{i}  \rho_2 b_k 
% - r_{k}r_{i}  \rho_2 b_j 
% } 
% \end{align*}
In, addition one must notice that the particle angular momentum balance equation doesn't involve the integral of the particle local stress and has therefore, no dynamical role in the equivalent stress expression. 
Making use of these remarks we obtain this general formula for the suspension stress,  
\begin{multline}
    \bm{\Sigma}
    = \avg{\rho\textbf{u}'\textbf{u}'}_{ik}
    + \phi_1 p_1 \delta_{ik}
    - \mu_1 e_{ik}
    % + \mu_1 \phi_2 e_{2,ik}. 
    - \pOavg{ \rho_2 (\textbf{w}_2^0\textbf{w}_2^0  )_{ik}}
    + \pavg{\ddt {\mathcal{S}_{ik}} }\\
    - \pSavg{ b_{i}r_k - b_{k}r_i }
    - \pSavg{ r_i (\bm{\sigma}_1^0 \cdot \textbf{n}_2)_{k}
    + r_k (\bm{\sigma}_1^0 \cdot \textbf{n}_2)_{i}}
    + \mu_1 \pOavg{e_2^0}_{ik}
    + \frac{1}{2} \div\bm{\Sigma}_1
    \label{eq:eq_stress}
\end{multline}
with the inhomogeneous stress gathered in $\bm{\Sigma}_1$, namely,
\begin{multline}
    \bm{\Sigma}_1
    = 
    - \pavg{\ddt\intO{ \rho_2 (\textbf{u}_2^0)_i r_j r_k }}
    + \pOavg{ \rho_2 (r_{j} (\textbf{w}_2^0)_k (\textbf{u}^0_2)_i + r_k (\textbf{w}_2^0)_j (\textbf{u}^0_2)_i)}\nonumber\\
    +\pSavg{  r_{k}r_{j} (\bm{\sigma}_1^0)_{il} (\textbf{n}_2)_l }
    - \mu_1 2 \pOavg{\textbf{r} \textbf{e}_2^0}_{jik}
\end{multline}
According to \ref{eq:scheme_equivalence}, expanding each component related to the dispersed phase in \ref{eq:momentum_bulk} one would see appear each moment of momentum equations under the divergence operator.
However, to stay consistent with the definition of the bulk stress tensor $\bm{\Sigma}$, we must keep the advecting term on the LHS of \ref{eq:momentum_bulk} unchanged, this is however not the case of the averaged body force term $\textbf{b}$ which allowed us to cancel all the body forces terms with the expansion of $\textbf{T}$.  

One of the major question in suspension dynamic raised by several authors, is the evaluation of the bulk stress or equivalent stress tensor of a suspension, see \citep{prosperetti2006stress, batchelor1970stress,zhang1997momentum,nadim1996concise} and more recently \citet{dolata2020heterogeneous}. 
The answer to this question is given in the general case of the generic averaged mixture equation. 
In light of \ref{eq:eq_stress} we have demonstrated how to express in a routine manner the bulk stress of the particle phase. 
And doing so without making appear explicitly the particles  internal stress. 
This, conclusion deserve several comments regarding previous studies. 
In  \citet{jackson1997locally},  the volume averaged momentum balance (equation (38) of \citet{jackson1997locally}) they make appear the higher moment of velocity of the particles as closure terms, these are hidden in $\pOavg{\textbf{w}_2^0 \textbf{w}_2^0}$.
However, in \citet{jackson1997locally} they did not remove the angular momentum to the stress yieldings a slightly different term. 
What we have shown here is that these higher moments of the particles phase such has the particles rotations have no dynamical significance in the mixture equations. 
Therefore, equation (38) of \citet{jackson1997locally} can be further simplified to the fluid and first order particle averaged equations. 
Equally, in the momentum mixture equation derived by \citet{zhang1997momentum} (equation (8.2)), they make appear explicitly the higher moment of acceleration and the higher moments of velocity in their equivalent stress. 
These terms must therefore simplify. 
In fact as, it could be supposed in their appendix these moments equally cancel. 
In agreement with \citet{dolata2021faxen} which also found that the only remaining part of the stress were solely the fluid phase exchange terms upon the calculation of the body forces moments. 
Similar, comments can be made on the study of \citet{prosperetti2006stress}. 
This also explain why \citet{nadim1996concise} found out that the interfacial terms of the surface tension and viscous interfacial forces play no direct role in the equivalent stress of the emulsion.